\documentclass[10pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,mathtools}
\usepackage{hyperref}
\usepackage{enumitem}

\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue}
\setlength{\parskip}{0.55em}
\setlength{\parindent}{0pt}
\setlength{\emergencystretch}{2em}

\newcommand{\Conf}{\mathrm{Conf}}

\title{A Narrow Note on the OPH Gravity Chain\\[0.3em]\large Isolating the Jacobson Route}
\author{B.\ Muller}
\date{\today}

\begin{document}
\maketitle

\begin{quote}\small
Observer-Patch Holography (OPH) contains a gravity branch written for readers already familiar with Jacobson's 1995 and 2016 entanglement-equilibrium arguments. The conditional chain isolated here is
\[
\begin{aligned}
\text{observer overlap}
&\to \text{modular cap geometry}
\to \text{null half-sided inclusion}
\to T_{kk} \\
&\to \delta S_{\mathrm{gen}}=0
\to G_{ab}+\Lambda g_{ab}=8\pi G\,\langle T_{ab}\rangle.
\end{aligned}
\]
The chain is conditional. In particular, fixed-cap generalized-entropy stationarity, the density upgrade to a local null stress, and the bounded-interval projective step used in the small-ball bridge remain explicit premises rather than derived outputs.

The same observer-overlap axiom package is also used elsewhere in the SM/GR derivation paper to support a conditional Lorentz branch, a schedule-independent overlap-consistency normal form, and a separate compact gauge-reconstruction branch targeting Standard Model structure.
\end{quote}

\section*{1. Cap Modular Geometry and the Lorentz Branch}

OPH starts from a net of patch algebras on a screen \(S^2\), overlap consistency of neighboring observers, a local MaxEnt/refinement-stable branch, and a recoverable generalized entropy functional. The gravity branch then takes a further scaling-limit premise: the refinement-stable cap net lies in the Bisognano--Wichmann geometric modular class.

For each cap \(C \subset S^2\), let \(\lambda_C(s) \subset \Conf^+(S^2)\) be the standard cap-preserving conformal subgroup, normalized so that the null blow-up near a smooth cut acts by
\[
v \mapsto e^{-s} v.
\]
If \(B_C\) is the infinitesimal generator of that geometric action, the OPH gravity theorem in the SM/GR derivation paper states
\[
K_C = 2\pi B_C,
\]
where \(K_C\) is the cap modular Hamiltonian on the OPH Bisognano--Wichmann branch.

This already gives the local kinematic group:
\[
\Conf^+(S^2) \cong \mathrm{PSL}(2,\mathbb C) \cong \mathrm{SO}^+(3,1).
\]
Hence, once cap modular flow is geometric in the stated scaling branch, the induced local kinematics is the connected Lorentz group.

\section*{2. Null Half-Lines and the Borchers Generator}

Next one blows up a cap near a smooth entangling cut and restricts to a chosen null generator \(\Omega\). Let \(v\) be an affine null coordinate with the cut at \(v=0\), and define the half-line algebras
\[
H_a := (a,\infty),
\qquad
\mathcal M_a(\Omega)
:=
\overline{\bigvee_{a<c<d<\infty}\mathcal A((c,d),\Omega)}.
\]

Because the cap modular action is geometric with the \(2\pi\) normalization, the blow-up modular action on the null coordinate is
\[
v \mapsto e^{-2\pi t} v,
\]
hence
\[
\sigma_t^\omega\bigl(\mathcal M_a(\Omega)\bigr)
=
\mathcal M_{e^{-2\pi t}a}(\Omega).
\]
For \(t \le 0\), this implies
\[
\sigma_t^\omega\bigl(\mathcal M_a(\Omega)\bigr) \subseteq \mathcal M_a(\Omega),
\]
so \(\mathcal M_a(\Omega) \subset \mathcal M_0(\Omega)\) is a half-sided modular inclusion.

At that point Borchers--Wiesbrock applies. One gets a unique strongly continuous unitary group
\[
U_\Omega(a) = e^{i a P_\Omega},
\qquad
P_\Omega \ge 0,
\]
with
\[
U_\Omega(a)\,\mathcal M_b(\Omega)\,U_\Omega(a)^* = \mathcal M_{a+b}(\Omega),
\]
and the affine covariance relation
\[
\Delta_0(\Omega)^{it} U_\Omega(a)\Delta_0(\Omega)^{-it}
=
U_\Omega(e^{-2\pi t} a).
\]
Differentiating gives
\[
[K_0(\Omega),P_\Omega] = -\,i\,2\pi P_\Omega,
\]
and for translated half-lines
\[
K_a(\Omega)=K_0(\Omega)-2\pi a\,P_\Omega.
\]

In the OPH chain, the positive null-translation generator is obtained from the cap blow-up geometry plus half-sided inclusion on the OPH scaling branch.

\section*{3. From the Half-Line Generator to Null Stress}

At this stage the chain has not yet reached the Einstein equation. In the SM/GR derivation paper, the half-line generator/charge identification is already fixed on the stated half-line family. What remains explicit downstream for the Jacobson step is the density upgrade together with the bounded-interval projective transport used in the small-ball bridge:
\[
\widetilde K[(a,\infty),\Omega]
=
2\pi\int_a^\infty (v-a)\,T_{kk}(v,\Omega)\,dv
+
E^{(\eta)}_{(a,\infty),\Omega}.
\]
Here \(E^{(\eta)}\) is a carried remainder controlled in matrix elements. The half-line generator/charge identification is not a separate relativistic EFT premise here; it is already fixed on the stated half-line family. What remains downstream is transport to bounded null intervals for the small-ball/Jacobson step, and the later tensor upgrade is still defined only modulo the null-invisible metric term.

Knowledge of \(T_{kk}\) in all null directions then determines the full stress tensor modulo a metric term: if a symmetric tensor \(X_{ab}\) obeys
\[
X_{ab} k^a k^b = 0
\]
for every null vector \(k\), then
\[
X_{ab} = \phi g_{ab}
\]
for some scalar \(\phi\).

So the null branch determines \(T_{ab}\) up to the usual \(\phi g_{ab}\) ambiguity, exactly the ambiguity that later shows up as the cosmological-constant term.

\section*{4. The Jacobson Step}

Now one specializes to the physical \(d=4\) scaling regime and considers a small cap \(C\). For admissible first-order state variations at fixed cap, fixed cap size or volume, and fixed conserved charges, OPH uses the first law
\[
\delta S_C = \delta \langle K_C\rangle = 2\pi\,\delta\langle B_C\rangle.
\]
It also uses the generalized-entropy split
\[
S_{\mathrm{gen}}(C)=S_{\mathrm{bulk}}(C)+\frac{A(C)}{4G}.
\]

The key extra premise is then stated plainly:
\[
\delta S_{\mathrm{gen}}(C)=0.
\]
This is the fixed-cap generalized-entropy stationarity assumption. OPH does \emph{not} claim to derive this from MaxEnt alone.

In the locally Lorentzian \(d=4\) small-ball regime, if \(\delta\langle T_{00}\rangle\) is approximately constant across a radius-\(\ell\) ball and the carried remainder contributes only \(o(\ell^4)\), the OPH small-ball lemma in the SM/GR derivation paper gives
\[
\delta S_{\mathrm{bulk}}(C)
=
\frac{8\pi^2 \ell^4}{15}\,\delta\langle T_{00}\rangle
+ O(\ell^5 \partial T)+o(\ell^4).
\]
For a fixed-volume small ball, the standard geometric variation is
\[
\delta A\big|_{V,\Lambda_{\mathrm{ref}}}
=
-\frac{4\pi \ell^4}{15}\,
\delta\!\left(G_{00}+\Lambda_{\mathrm{ref}} g_{00}\right).
\]

Putting these into \(\delta S_{\mathrm{gen}}=0\) gives
\[
0
=
\frac{8\pi^2 \ell^4}{15}\,\delta\langle T_{00}\rangle
-\frac{\pi \ell^4}{15G}\,
\delta\!\left(G_{00}+\Lambda_{\mathrm{ref}} g_{00}\right)
+ O(\ell^5 \partial T)+o(\ell^4).
\]
Dividing by \(\ell^4\) and taking the small-ball limit yields the rest-frame relation
\[
\delta\!\left(G_{00}+\Lambda g_{00}\right)
=
8\pi G\,\delta\langle T_{00}\rangle.
\]

Finally, overlap consistency across observers through the same point supplies all local timelike directions. Combined with the null reconstruction lemma above, this upgrades the rest-frame statement to
\[
G_{ab}+\Lambda g_{ab}=8\pi G\,\langle T_{ab}\rangle
\]
modulo the already isolated metric-term ambiguity.

\section*{5. What Is Borrowed and What Is OPH-Specific}

\textbf{Imported mathematical or physical ingredients}
\begin{itemize}[leftmargin=1.8em]
\item Bisognano--Wichmann geometric modular action and the \(2\pi\) normalization.
\item Borchers--Wiesbrock half-sided modular inclusion and the resulting positive translation generator.
\item Jacobson's small-ball first-law or entanglement-equilibrium step from \(\delta S_{\mathrm{gen}}=0\) to the Einstein relation.
\end{itemize}

\textbf{What OPH is trying to add}
\begin{itemize}[leftmargin=1.8em]
\item A concrete observer-patch framework in which caps are primary objects and overlap consistency is the organizing principle.
\item A route from cap modular geometry to a null half-line modular pair, with half-sided inclusion derived from cap blow-up geometry.
\item An all-directions upgrade driven by overlap consistency across neighboring observers.
\item One shared axiom package: in the SM/GR derivation paper the same observer-overlap structure is also used for the Lorentz branch, the overlap-repair normal form, and a separate gauge-reconstruction program aimed at Standard Model structure.
\item A dependency ledger that keeps the remaining burdens explicit instead of treating them as already solved.
\end{itemize}

\textbf{The remaining explicit burdens}
\begin{itemize}[leftmargin=1.8em]
\item the geometric modular branch assumption on the refinement limit;
\item the density upgrade from weak endpoint derivatives to a local null density;
\item the relativistic identification of that density with continuum \(T_{kk}\);
\item the fixed-cap stationarity premise \(\delta S_{\mathrm{gen}}=0\).
\end{itemize}

The resulting conditional Jacobson branch is the mathematical object isolated by this note.

\section*{References}

\begingroup\small
\begin{enumerate}[leftmargin=1.8em,itemsep=0.15em]
\item T.~Jacobson, ``Thermodynamics of spacetime: The Einstein equation of state,'' \emph{Phys.\ Rev.\ Lett.}\ 75 (1995), 1260--1263.
\item T.~Jacobson, ``Entanglement equilibrium and the Einstein equation,'' \emph{Phys.\ Rev.\ Lett.}\ 116 (2016), 201101.
\item J.~J.~Bisognano and E.~H.~Wichmann, ``On the duality condition for quantum fields,'' \emph{J.\ Math.\ Phys.}\ 17 (1976), 303--321.
\item H.-W.~Wiesbrock, ``Half-sided modular inclusions of von Neumann algebras,'' \emph{Commun.\ Math.\ Phys.}\ 157 (1993), 83--92.
\end{enumerate}
\endgroup

\end{document}
