\section{Supplemented Gravity and Structural Gauge Details}
\label{app:compact-technical-port}

This appendix carries the gravity-side and structural gauge items that support the compact paper's
technical surface. They sharpen the compact paper's Lorentz,
Einstein, cosmological-constant, and product-group claim surfaces without widening the recovered
core beyond its stated premises.

\subsection{Lorentz and Einstein Bridge}

\begin{theorem}[Conformal group isomorphism]
The orientation-preserving conformal group of \(S^2\) is isomorphic to the connected Lorentz
group:
\[
\mathrm{Conf}^+(S^2)\cong \mathrm{PSL}(2,\mathbb C)\cong \mathrm{SO}^+(3,1).
\]
\end{theorem}

\begin{theorem}[Geometric modular flow on caps on the extracted prime geometric subnet]
Assume the OPH axioms, the derived fixed-cutoff collar package, the controlled scaling-limit
scope clause \textbf{T2}, and the theorem-local realized geometric cap-pair extraction plus
ordered cut-pair rigidity hypotheses on the extracted prime geometric subnet. Then the
scaling-limit modular automorphism group of the cap pair is geometric conformal dilation on that
subnet, with the standard \(2\pi\) normalization. If the emitted scaling-limit cap algebra
is type I, this may be written as \(K_C=2\pi B_C\); in the generic continuum case the
theorem is the automorphism statement on a non-type-I cap algebra with outer geometric modular
action.
\end{theorem}

\paragraph{BW-side UV scaffold.}
The UV burden on this branch is not a separate cap-isotropy or Euclidean-regularity
selector. The fixed-cutoff cap algebras are type-I regulators, but the scaling-limit observer
algebra may leave that class, and MaxEnt alone does not select the BW / canonical cap phase. The
UV burden is the realized transported geometric cap-local system together with the
carried-collar schedule derived from the transported fixed-local-collar Markov/faithfulness datum
on each fixed local collar model, followed by ordered cut-pair rigidity on the emitted
scaling-limit geometric cap pair.

\paragraph{Null-strip completion status.}
On the D4 side, the fixed-cutoff strip package is more specific than the generic inherited-strip summary.
The null cuts first transfer the same cut-center data as the spatial collar branch, which fixes
the central sector-pair decomposition of the strip algebra. The stronger left/right tensor
decomposition used by the null modular bridge then requires the extra inherited strip-split
condition on the multiplicity spaces, together with the exact-or-controlled Markov hypotheses on
one fixed inherited strip model. On that same fixed strip model, the renormalized half-line family
is endpoint-Lipschitz, hence defines the weak tail generator, and on the scaling-limit
geometric-cap branch the half-line blow-up net carries the derived half-sided modular pair.
Borchers--Wiesbrock then supplies the positive null-translation generator on its Stone domain
together with the affine half-line modular relation \(K_a(\Omega)=K_0(\Omega)-2\pi aP_\Omega\).
Bounded-interval formulas are downstream on the separate interval-preserving projective branch.

\begin{lemma}[Null data ambiguity]
If a symmetric tensor \(X_{ab}\) satisfies
\[
X_{ab}k^ak^b=0
\]
for every null vector \(k\), then \(X_{ab}=\phi\,g_{ab}\) for some scalar \(\phi\).
\end{lemma}

\begin{corollary}[Null modular data determine Einstein only up to the metric term]
Null modular data determine \(T_{ab}\) only up to \(\phi g_{ab}\). Consequently the Einstein
equation is fixed locally only up to \(\Lambda g_{ab}\).
\end{corollary}

\begin{theorem}[Conditional Jacobson-type rest-frame relation]
In the local Lorentzian scaling regime, once the realized cap-label-preserving MaxEnt family satisfies the derived fixed-cap generalized-entropy stationarity theorem for admissible fixed-cap variations, the half-line
generator/charge identification of the null bridge, the bounded-interval transport input used in
the local Lorentzian regime, and the internal small-ball bridge yield the rest-frame first-variation
relation that drives the compact paper's local Einstein branch; on the same scaling branch, if that
rest-frame relation holds for all local observer four-velocities and all reference states, the
compact paper upgrades it to the full tensor equation by the explicit local quadratic-polarization
argument of Corollary~\ref{cor:einstein}.
\end{theorem}

\begin{theorem}[Newton coupling from edge entropy density]
The gravitational coupling is fixed by the edge entropy density:
\[
G=\frac{a_{\mathrm{cell}}}{4\bar{\ell}(t)}.
\]
\end{theorem}

\subsection{Cosmological-Constant / Screen-Capacity Closure}

\begin{lemma}[Vacuum energy blindness]
For any null vector \(k\),
\[
T^{\mathrm{vac}}_{kk}
=
T^{\mathrm{vac}}_{ab}k^ak^b
=
-\rho_{\mathrm{vac}}\,g_{ab}k^ak^b
=
0.
\]
Vacuum-energy contributions therefore lie in the kernel of the null map
\(T_{ab}\mapsto T_{kk}\).
\end{lemma}

\begin{proposition}[Structural separation]
Within the structural split used here:
\begin{enumerate}[leftmargin=2em]
\item local modular/null data fix \(T_{ab}\) only up to \(\phi g_{ab}\); and
\item \(\Lambda\) is fixed by global screen capacity, not by local null data.
\end{enumerate}
So the large vacuum-energy bookkeeping of EFT is not itself the local quantity determining
curvature on this branch.
\end{proposition}

\begin{theorem}[No local \(\Lambda\) prediction]
Within the null-modular reconstruction used here:
\begin{enumerate}[leftmargin=2em]
\item all \(T_{kk}\) data are unchanged under \(T_{ab}\to T_{ab}+\phi g_{ab}\);
\item therefore \(\Lambda\) cannot be fixed by local overlap consistency alone; and
\item \(\Lambda\) requires the global screen-capacity input that closes the same Einstein branch beyond the local null data.
\end{enumerate}
\end{theorem}

\begin{corollary}[Benchmark cosmological readout on the D6 branch]\label{cor:lambda-benchmark}
On the same D6 branch as Corollaries~\ref{cor:lambda}--\ref{cor:lambda-parameters}, inserting the observed value \(\Lambda\approx 1.09\times 10^{-52}\,\mathrm{m^{-2}}\) gives
\[
r_{\mathrm{dS}}=\sqrt{\frac{3}{\Lambda}}\approx 1.66\times 10^{26}\ \mathrm{m},
\qquad
t_\Lambda=\frac{r_{\mathrm{dS}}}{c}\approx 17.5\ \mathrm{Gyr},
\]
\[
N_{\mathrm{scr}}\approx 2.85\times 10^{122}.
\]
\end{corollary}

\begin{proof}
Immediate from Corollary~\ref{cor:lambda-parameters}.
\end{proof}

\paragraph{Observed-age benchmark status.}
The branch quantity \(t_\Lambda\) is the de Sitter static-patch timescale. The usual cosmic age \(t_0\) is a compare-only FLRW benchmark rather than an additional D6 theorem output. On the flat \(\Lambda\)CDM benchmark
\[
t_0=\frac{2}{3H_0\sqrt{\Omega_\Lambda}}
\sinh^{-1}\!\left(\sqrt{\frac{\Omega_\Lambda}{\Omega_m}}\right)
\]
one gets the standard comparison value \(t_0\approx 13.8\,\mathrm{Gyr}\) at
\(H_0\approx 67.4\,\mathrm{km\,s^{-1}\,Mpc^{-1}}\) and \(\Omega_\Lambda\approx 0.685\).

\begin{theorem}[D5--D6 cosmological-capacity closure stack]
Assume the compact paper's local Einstein branch, the external input
\[
N_{\mathrm{scr}}=\log \dim \mathcal H_{\mathrm{tot}},
\]
the D6 screen-capacity identification
\[
N_{\mathrm{scr}}=S_{\mathrm{dS}},
\]
\noindent the standard de Sitter entropy relation
\[
S_{\mathrm{dS}}=\frac{A_{\mathrm{dS}}}{4G}=\frac{3\pi}{G\Lambda},
\]
and the standard static-patch formulas
\[
r_{\mathrm{dS}}=\sqrt{\frac{3}{\Lambda}},
\qquad
t_\Lambda=\frac{r_{\mathrm{dS}}}{c}.
\]
Then the cosmological-constant package is one local/global theorem stack: local null data fix the
Einstein branch only modulo \(\Lambda g_{ab}\), the same branch closes globally as
\[
G_{ab}+\frac{3\pi}{G N_{\mathrm{scr}}}\,g_{ab}=8\pi G\,\langle T_{ab}\rangle,
\]
the same D6 closure fixes
\[
S_{\mathrm{dS}}=N_{\mathrm{scr}},
\qquad
A_{\mathrm{dS}}=4G N_{\mathrm{scr}},
\qquad
r_{\mathrm{dS}}=\sqrt{\frac{3}{\Lambda}},
\qquad
t_\Lambda=\frac{r_{\mathrm{dS}}}{c},
\]
and the observed cosmic age is a downstream FLRW benchmark rather than an additional theorem
output.
\end{theorem}

\paragraph{Scope boundary.}
The imported premises are exactly the D5 local Einstein branch, the external input
\(N_{\mathrm{scr}}\), the D6 identification \(N_{\mathrm{scr}}=S_{\mathrm{dS}}\), the standard de
Sitter entropy relation, and the standard static-patch formulas. The external item is the
screen-capacity identification itself; it is not derived from the bare local null-data route.

\paragraph{Separate pixel-side benchmarks.}
The companion pixel numbers
\[
a_{\mathrm{cell}}\approx 1.63\,\ell_P^2,
\qquad
\ell_{\mathrm{UV}}=\sqrt{a_{\mathrm{cell}}}\approx 1.28\,\ell_P,
\qquad
\bar{\ell}\approx 0.408
\]
belong to the separate pixel-closure/local-readout package rather than to the D6 cosmological-parameter corollary itself.

\subsection{Product-Group Structural Corollaries}

\begin{theorem}[Factorization equivalence]
\[
\text{Factorizing edge weights}
\Longleftrightarrow
\text{Additive boundary Laplacian}
\Longleftrightarrow
\text{Product gauge group}.
\]
If
\[
H_\partial=H_\partial^{(1)}+H_\partial^{(2)}+H_\partial^{(3)}
\qquad\text{with}\qquad
[H_\partial^{(i)},H_\partial^{(j)}]=0,
\]
then
\[
p(R_1,R_2,R_3)\propto\prod_{i=1}^3 d_{R_i}e^{-t_iC_2(R_i)}.
\]
Applied to the assumed transportable refinement-directed edge-sector colimit on the realized
branch, together with the rigid symmetric
\(C^*\)-tensor and faithful bosonic fiber-functor premises of the compact-gauge theorem,
Tannaka--Krein reconstruction first yields some compact group \(G\). Under the MAR admissibility
package, and once the admissible class includes one connected abelian charge factor, the selected
connected Lie realization is \(SU(3)\times SU(2)\times U(1)\) up to finite quotient.
\end{theorem}

\begin{corollary}[No leptoquarks, hence no gauge-mediated proton decay]
With product gauge group, the adjoint representation of the full connected gauge group is
\[
(8,1,0)\oplus(1,3,0)\oplus(1,1,0),
\]
equivalently the derived nonabelian adjoint is
\[
(8,1,0)\oplus(1,3,0).
\]
There are therefore no gauge generators in mixed representations \((3,2,\pm 5/6)\), i.e. no
simple-GUT \(X,Y\) bosons on the realized branch. The structural claim is exactly
\[
\tau_p^{(\mathrm{gauge})}=\infty,
\]
meaning that the gauge-boson proton-decay channel is absent. Scalar-mediated or
higher-dimensional baryon-violating operators are outside this structural corollary.
\end{corollary}

\paragraph{Proton-spin continuation benchmark.}
On the realized D8--D9 branch the color factor is \(\mathrm{SU}(3)\), so the structural OPH
input for proton-spin bookkeeping is
\[
C_F=\frac43,
\qquad
C_A=3.
\]
If one adds the QCD-dependent continuation ansatz that quark/gluon spin sharing equilibrates
according to these Casimirs, then
\[
\Delta\Sigma\approx \frac{C_F}{C_F+C_A}=\frac{4}{13}\approx 0.308.
\]
Against a representative lattice benchmark \(\Delta\Sigma\approx 0.286\), this lands within about
\(8\%\), but it is only a deferred continuation benchmark. A first-principles OPH derivation of
proton spin would require the nonperturbative light-quark/hadron completion plus an explicit map
from OPH data to renormalized proton matrix elements.

\subsection{Controlled Worldsheet Effective Description}

\paragraph{Exact OPH-to-2D-Yang--Mills bridge.}
On the compact-group heat-kernel branch, Theorem~\ref{thm:edge-2dym} proves the exact identity
\[
Z_{\mathrm{edge}}(t)=K_t(1)
\]
by gluing the open-edge weights \(p_R(t)\propto d_R e^{-tC_2(R)}\) into the closed partition sum
\[
Z_{\mathrm{edge}}(t)=\sum_R d_R^2 e^{-tC_2(R)}.
\]
This is the precise theorem-level sense in which the OPH edge-sector partition reorganizes into
the two-dimensional Yang--Mills heat-kernel surface, and the Chapman--Kolmogorov law supplies the
matching collar-sewing rule.

\paragraph{Large-\(N_{\mathrm{edge}}\) boundary.}
The large-\(N_{\mathrm{edge}}\)
worldsheet interpretation is carried only when one fixes a distinct large-\(N_{\mathrm{edge}}\)
sequence, with \(N_{\mathrm{edge}}\neq N_c=3\), a fixed-\(\tau\) window for
\[
\tau=tN_{\mathrm{edge}},
\]
and the uniform genus-remainder control of Theorem~\ref{thm:worldsheet-largeN}. On that branch the
edge free energy satisfies the compact paper's theorem-level criterion for a controlled genus
expansion, so the standard Gross--Taylor rewriting becomes a controlled worldsheet effective
description of edge dynamics rather than a loose analogy.

\paragraph{External items.}
The exact bridge theorem does not derive the compact-group heat-kernel branch itself from bare
local axioms, and the continuation theorem does not derive the large-\(N_{\mathrm{edge}}\) regime
itself, nor does
it rederive the imported Gross--Taylor large-\(N\) worldsheet dictionary for two-dimensional
Yang--Mills, nor does it identify a critical worldsheet CFT. Worldsheet supersymmetry, critical
dimension, modular invariance, anomaly cancellation, GSO projection, and full massless-spectrum
matching is separate extra premises beyond the compact recovered-core chain.
