\section{Formal Measurement / Markov / Born-L\"uders Ledger}
\label{app:microphysics-measurement-ledger}

This appendix carries the formal measurement-theory block for the microphysics paper. It sharpens
the fixed-cutoff
record interface used in the main theorem packages above. The theorem-bearing leaf-level
closure is the main-text fixed-cutoff central-record / Born-L\"uders package; this appendix is
the supporting ledger and comparison surface, not a replacement theorem surface.

\subsection{Records as Central Variables}

\textbf{Definition.} On one completed observer-facing slice in patch \(P\), an \emph{exact record
presentation} is a family of orthogonal projectors
\(\{\widehat\Pi_r\}\subset Z(\mathcal A(P))\) whose generated algebra
\[
\mathcal R:=\mathrm{vN}(\{\widehat\Pi_r\})
\]
is finite and commutative. A \emph{practical record presentation} is a family of projectors
\(\{\Pi_r\}\subset\mathcal A(P)\) on the same declared slots such that
\[
\delta_{\mathrm{rec}}:=\max_r \|\Pi_r-\widehat\Pi_r\|
\]
is finite. The exact central presentation carries the theorem-bearing fixed-cutoff measurement
surface; the practical presentation records controlled readout error above it. The declared record
surface must also satisfy:
\begin{enumerate}[leftmargin=2em]
\item \textbf{Stability:} the declared readout projectors on that slice are stable under the effective fixed-cutoff dynamics.
\item \textbf{Shareability:} each \(\widehat\Pi_r\) lies in the center of the relevant overlap algebra.
\end{enumerate}

\paragraph{\textbf{Proposition 3.0 (Quantitative record stability).}}
For a practical record presentation on the same declared slots,
\[
\|[\Pi_r,\Pi_s]\|\le 4\,\delta_{\mathrm{rec}}
\]
for all \(r,s\). If \(\|\widetilde\rho-\rho\|_1\le\varepsilon\), then each declared elementary
record-event probability obeys
\[
\Bigl|
\operatorname{Tr}(\widetilde\rho\,\Pi_r)
-
\operatorname{Tr}(\rho\,\widehat\Pi_r)
\Bigr|
\le
\varepsilon+\delta_{\mathrm{rec}}.
\]

\paragraph{\textbf{Proof sketch.}}
Because \([\widehat\Pi_r,\widehat\Pi_s]=0\), one writes
\[
[\Pi_r,\Pi_s]
=
[\Pi_r-\widehat\Pi_r,\Pi_s]
+
[\widehat\Pi_r,\Pi_s-\widehat\Pi_s],
\]
and bounds each term by twice the corresponding operator-norm error. The probability estimate is
the same two-term decomposition used on the main-text record surface:
\[
\operatorname{Tr}(\widetilde\rho\,\Pi_r)-\operatorname{Tr}(\rho\,\widehat\Pi_r)
=
\operatorname{Tr}((\widetilde\rho-\rho)\Pi_r)
+
\operatorname{Tr}(\rho(\Pi_r-\widehat\Pi_r)),
\]
so trace-norm control contributes \(\varepsilon\) and projector error contributes
\(\delta_{\mathrm{rec}}\).

\subsection{Markov Structure and Recoverability}

\paragraph{\textbf{Theorem 3.1 (Quantum Markov chain structure on a fixed EC collar).}}
If \(I(A:C\mid B)=0\) for a tripartite state \(\rho_{ABC}\), then
\[
\mathcal H_B
\cong
\bigoplus_j
\left(
\mathcal H_{b_L^{(j)}}\otimes \mathcal H_{b_R^{(j)}}
\right)
\]
and the state decomposes as
\[
\rho_{ABC}
=
\bigoplus_j
q_j\,
\rho^{(j)}_{A b_L^{(j)}}\otimes \rho^{(j)}_{b_R^{(j)} C}.
\]
The label \(j\) is a classical variable living in the center of \(\mathcal A(B)\).

On the fixed finite-dimensional collar Hilbert space supplied by EC, let
\[
\mathfrak M_{A:B:C}
:=
\left\{
\sigma_{ABC}: I(A:C\mid B)_\sigma=0
\right\}
\]
and define the exact-Markov distance modulus
\[
\delta^{\mathrm M}_{A:B:C}(\varepsilon)
:=
\sup\left\{
\inf_{\sigma\in\mathfrak M_{A:B:C}}\|\rho-\sigma\|_1:
I(A:C\mid B)_\rho\le\varepsilon
\right\}.
\]
Because the state space is compact and conditional mutual information is continuous in finite
dimension,
\[
\delta^{\mathrm M}_{A:B:C}(\varepsilon)\longrightarrow0
\qquad
(\varepsilon\downarrow0).
\]
Approximate collars therefore converge to the exact HJPW normal form on one fixed
finite-dimensional collar model or on a compatible pulled-back family. This appendix does not
claim a universal dimension-free one-shot trace-norm bound from small \(I(A:C\mid B)\) directly
to an exact Markov state.

\paragraph{\textbf{Theorem 3.2 (Fawzi--Renner recovery).}}
If
\[
I(A:C\mid B)_\rho\le\varepsilon,
\]
then there exists a CPTP map \(\mathcal R:\mathcal A(B)\to\mathcal A(BC)\) such that the
recovered comparison state
\[
\rho^{\mathrm{rec}}_{ABC}
:=
(\mathrm{id}_A\otimes\mathcal R)(\rho_{AB})
\]
obeys
\[
\|\rho_{ABC}-\rho^{\mathrm{rec}}_{ABC}\|_1
\le
2\sqrt{1-e^{-\varepsilon}}
\le
2\sqrt{\varepsilon}.
\]
If \(\varepsilon\) is quoted in bits rather than nats, this bound is equivalently written as
\(2\sqrt{\ln 2\,\varepsilon}\).

The recovered state is a constructive comparison state and need not be exact Markov. To connect
approximate recoverability to the exact splice or additivity formulas used later, one combines the
recovery theorem with the fixed-collar modulus above. Concretely, if
\(\sigma_\varepsilon\in\mathfrak M_{A:B:C}\) is chosen so that
\[
\|\rho-\sigma_\varepsilon\|_1
\le
\delta^{\mathrm M}_{A:B:C}(\varepsilon),
\]
then every bounded observable supported on the left side of the collar differs from its exact
Markov splice value by at most
\[
\|X\|_\infty\,\delta^{\mathrm M}_{A:B:C}(\varepsilon),
\]
and, under uniform faithfulness with lower spectral bound \(\lambda_\ast>0\), the corresponding
modular-additivity defect differs from the exact Markov value by at most
\[
4\lambda_\ast^{-1}\,\delta^{\mathrm M}_{A:B:C}(\varepsilon).
\]
So the microphysics paper keeps two distinct errors visible:
\[
r_{\mathrm{FR}}(\varepsilon)=O(\varepsilon^{1/2}),
\qquad
\delta^{\mathrm M}_{A:B:C}(\varepsilon)\to0.
\]

\subsection{Definiteness, Born, and Conditioning}

\paragraph{\textbf{Theorem 3.3 (Collapse from EC structure).}}
Under EC, the post-measurement physical state is exactly a convex mixture over sector labels
\(\alpha\):
\[
\rho=\bigoplus_\alpha p_\alpha\,\rho^{(\alpha)}.
\]
For any observer whose accessible observables lie in either side algebra:
\begin{enumerate}[leftmargin=2em]
\item there are no interference observables between different \(\alpha\)-blocks; and
\item each observer-instance has a definite \(\alpha\) in the classical sense.
\end{enumerate}
Cross-block operators \(|i\rangle\langle j|\) for \(i\in\alpha\), \(j\in\alpha'\), and
\(\alpha\neq\alpha'\) are not gauge-invariant and therefore do not belong to the physical algebra.

\paragraph{\textbf{Theorem 3.4 (Gleason).}}
For \(\dim \mathcal H\ge 3\), any measure \(\mu\) on projectors satisfying:
\begin{enumerate}[leftmargin=2em]
\item noncontextuality: \(\mu(P)\) depends only on \(P\);
\item additivity: \(\mu(P\vee Q)=\mu(P)+\mu(Q)\) for \(P\perp Q\); and
\item normalization: \(\mu(\mathbf 1)=1\),
\end{enumerate}
must have the form
\[
\mu(P)=\operatorname{Tr}(\rho P)
\]
for some density operator \(\rho\).

\paragraph{\textbf{Corollary 3.5 (Born uniqueness on the fixed-cutoff record surface).}}
Within the fixed-cutoff type-I regulator presentation used here, Born's rule is the unique
overlap-consistent probability assignment on the record algebra.

\paragraph{\textbf{Proposition 3.6 (Luders update).}}
For record projectors \(\{\Pi_r\}\) and state \(\omega\),
\[
p_r=\omega(\Pi_r),
\qquad
\omega_r(X)=\frac{\omega(\Pi_r X \Pi_r)}{\omega(\Pi_r)}.
\]
Then for all \(X\) commuting with the record algebra \(\mathcal R\),
\[
\omega(X)=\sum_r p_r\,\omega_r(X).
\]
So collapse on the observer-facing fixed-cutoff surface is simply classical conditioning on the
commuting record algebra.

\subsection{Two-Wing Bell / CHSH Package}

\textbf{Definition.} On one declared fixed-cutoff physical observable algebra
\(\mathcal A_{\mathrm{phys}}(L\cup R)\), a \emph{two-wing Bell presentation} consists of:
\begin{enumerate}[leftmargin=2em]
\item commuting left/right wing subalgebras
\[
\mathcal A_L,\mathcal A_R\subset \mathcal A_{\mathrm{phys}}(L\cup R),
\qquad
[X_L,X_R]=0
\quad
\forall\,X_L\in\mathcal A_L,\ X_R\in\mathcal A_R;
\]
\item central classical setting values \(x,y\in\{0,1\}\) on the declared record slots;
\item binary projective readouts
\[
\{P_{a|x}^{(L)}\}_{a=\pm1}\subset\mathcal A_L,
\qquad
\{P_{b|y}^{(R)}\}_{b=\pm1}\subset\mathcal A_R,
\]
with orthogonality and completeness on each wing; and
\item a physical source state \(\rho_{LR}\) on \(\mathcal A_{\mathrm{phys}}(L\cup R)\).
\end{enumerate}
The source-state premise is explicit. This appendix does not derive Bell-pair preparation from
bare repair dynamics.

\paragraph{\textbf{Theorem 3.7 (Fixed-cutoff Bell law and no-signaling).}}
For a two-wing Bell presentation, define
\[
\Pi_{ab|xy}:=P_{a|x}^{(L)}P_{b|y}^{(R)}.
\]
Then
\[
p(a,b\mid x,y)
=
\operatorname{Tr}\!\bigl(\rho_{LR}\,\Pi_{ab|xy}\bigr)
=
\operatorname{Tr}\!\bigl(\rho_{LR}\,P_{a|x}^{(L)}P_{b|y}^{(R)}\bigr)
\]
is a probability law on \(\{ \pm1\}\times\{\pm1\}\), and
\[
\sum_{b=\pm1} p(a,b\mid x,y)
=
\operatorname{Tr}\!\bigl(\rho_{LR}\,P_{a|x}^{(L)}\bigr),
\qquad
\sum_{a=\pm1} p(a,b\mid x,y)
=
\operatorname{Tr}\!\bigl(\rho_{LR}\,P_{b|y}^{(R)}\bigr).
\]
Hence the local marginal on one wing is independent of the remote setting.

\paragraph{\textbf{Proof sketch.}}
Because the left/right projectors commute, \(\{\Pi_{ab|xy}\}_{a,b}\) is a commuting projective
family on the fixed setting slice. The Born trace therefore gives the joint law. Positivity is
immediate, normalization follows from the completeness relations, and summing over one wing
removes the remote projector.

\paragraph{\textbf{Theorem 3.8 (CHSH/Tsirelson on the fixed-cutoff Bell surface).}}
Define
\[
A_x:=P_{+|x}^{(L)}-P_{-|x}^{(L)},
\qquad
B_y:=P_{+|y}^{(R)}-P_{-|y}^{(R)}.
\]
Then
\[
A_x^2=\mathbf 1,
\qquad
B_y^2=\mathbf 1,
\qquad
[A_x,B_y]=0,
\]
and the Bell correlators satisfy
\[
E(x,y)
:=
\sum_{a,b=\pm1}ab\,p(a,b\mid x,y)
=
\operatorname{Tr}\!\bigl(\rho_{LR}\,A_xB_y\bigr).
\]
For the CHSH operator
\[
\mathcal B:=A_0(B_0+B_1)+A_1(B_0-B_1)
\]
one has
\[
\mathcal B^2
=
4\,\mathbf 1-[A_0,A_1][B_0,B_1],
\qquad
\|\mathcal B\|\le 2\sqrt2.
\]
Therefore
\[
\bigl|E(0,0)+E(0,1)+E(1,0)-E(1,1)\bigr|
\le
2\sqrt2.
\]

\paragraph{\textbf{Proof sketch.}}
Expand \(A_xB_y\) in the projective basis to get the correlator formula. Expand \(\mathcal B^2\)
and use \(A_x^2=B_y^2=\mathbf 1\) together with \([A_x,B_y]=0\). Since
\(\|[A_0,A_1]\|\le 2\) and \(\|[B_0,B_1]\|\le 2\), the operator norm of \(\mathcal B^2\) is at
most \(8\).

\paragraph{\textbf{Corollary 3.9 (Two-qubit saturation branch).}}
Assume additionally that there exist commuting unital \(*\)-subalgebras
\[
\mathcal Q_L\subset \mathcal A_L,
\qquad
\mathcal Q_R\subset \mathcal A_R,
\]
with
\[
\mathcal Q_L\cong M_2(\mathbb C),
\qquad
\mathcal Q_R\cong M_2(\mathbb C),
\qquad
C^*(\mathcal Q_L,\mathcal Q_R)\cong M_2(\mathbb C)\otimes M_2(\mathbb C).
\]
Assume that, under this identification, the restriction of \(\rho_{LR}\) to
\(C^*(\mathcal Q_L,\mathcal Q_R)\) is
\[
|\Phi^+\rangle\!\langle\Phi^+|,
\qquad
|\Phi^+\rangle=\frac{|00\rangle+|11\rangle}{\sqrt2},
\]
and that the fixed-cutoff observables restrict there to
\[
A_0=\sigma_z\otimes \mathbf 1,
\qquad
A_1=\sigma_x\otimes \mathbf 1,
\]
\[
B_0=\mathbf 1\otimes \frac{\sigma_z+\sigma_x}{\sqrt2},
\qquad
B_1=\mathbf 1\otimes \frac{\sigma_z-\sigma_x}{\sqrt2}.
\]
Then
\[
E(0,0)=E(0,1)=E(1,0)=\frac{1}{\sqrt2},
\qquad
E(1,1)=-\frac{1}{\sqrt2},
\]
and hence
\[
E(0,0)+E(0,1)+E(1,0)-E(1,1)=2\sqrt2.
\]

\paragraph{\textbf{Proof sketch.}}
This is the standard two-qubit computation on the explicitly assumed
\(M_2(\mathbb C)\otimes M_2(\mathbb C)\) subalgebra. It is an exact branch-conditional statement
on that added two-qubit premise; it does not derive tensor-factor structure or Bell-pair
preparation from the bare OPH repair dynamics.
