\section{Cosmology, Horizons, and Modular-Anomaly Continuations}
\label{app:observers-cosmology-port}

This appendix rehouses the cosmology- and continuation-facing technical statements that had been
living in the former standalone technical supplement. They do not enlarge the recovered core; they
make the structural continuation boundary explicit on the live synthesis surface.

\subsection{Cosmological Principle}

\paragraph{\textbf{Lemma 4.1 (MaxEnt symmetry inheritance).}}
Let \(G\) act on the screen by automorphisms \(\alpha_g\). If the constraint set is
\(G\)-invariant and von Neumann entropy is \(G\)-invariant, then the MaxEnt optimizer \(\omega\)
can be taken \(G\)-invariant. If the optimizer is unique, it is automatically \(G\)-invariant.

\paragraph{\textbf{Theorem 4.2 (Isotropy from SO(3)-invariant constraints).}}
Under SO(3)-invariant constraints and MaxEnt uniqueness, the reference state satisfies
\[
\omega\circ\alpha_g=\omega
\qquad
\forall g\in \mathrm{SO}(3).
\]
The corresponding stress tensor has perfect-fluid form:
\[
\langle T_{ab}\rangle=\rho\,u_au_b+p(g_{ab}+u_au_b).
\]

\paragraph{\textbf{Theorem 4.3 (Schur-type homogeneity).}}
Let \((\Sigma,h_{ij})\) be a three-dimensional Riemannian manifold. If at every point
\(p\in\Sigma\), the curvature tensor is SO(3)-invariant, then
\[
R_{ijkl}(p)=K(p)(h_{ik}h_{jl}-h_{il}h_{jk}),
\]
and the second Bianchi identity forces \(\nabla_m K=0\), so \(K\) is constant.

\paragraph{\textbf{Corollary 4.4.}}
If OPH supplies isotropy for all observers, spatial geometry is a constant-curvature space form:
\(S^3\), \(\mathbb R^3\), or \(H^3\).

\paragraph{\textbf{Theorem 4.5 (FLRW emergence).}}
With the semiclassical Einstein equation from recoverable generalized entropy / entanglement
equilibrium, a perfect-fluid stress tensor from SO(3)-invariant MaxEnt, and positive \(\Lambda\)
from finite screen capacity, the emergent geometry is FLRW:
\[
ds^2=-dt^2+a(t)^2\left(\frac{dr^2}{1-kr^2}+r^2d\Omega^2\right),
\]
with Friedmann equations
\[
H^2+\frac{k}{a^2}=\frac{8\pi G}{3}\rho+\frac{\Lambda}{3},
\qquad
\dot H-\frac{k}{a^2}=-4\pi G(\rho+p).
\]

\subsection{Horizon-Problem Control}

\paragraph{\textbf{Theorem 6.1 (Anisotropy bound from Markov control).}}
For a tripartition \(A\)-\(B\)-\(D\) with collar width \(\delta\), the Markov error satisfies
\[
I(A:D\mid B)\lesssim c\cdot |\partial C|_{\mathrm{UV}}\cdot e^{-\delta/\xi},
\]
where \(\xi\) is the correlation length.

\paragraph{\textbf{Corollary 6.2.}}
For bounded observable \(O\) with \(\|O\|\sim1\),
\[
|\Delta\langle O\rangle|\le 2\sqrt{\ln 2\cdot \varepsilon}.
\]
On the CMB anisotropy target \(\delta T/T\lesssim 10^{-5}\), this gives the familiar
\(\varepsilon\)-scale bound used in the horizon-problem bookkeeping:
\[
\varepsilon\lesssim 3.61\times 10^{-11}\ \text{bits},
\qquad
\frac{\delta}{\xi}\gtrsim
\ln\!\left(\frac{c\cdot |\partial C|_{\mathrm{UV}}}{\varepsilon_{\max}}\right)\approx 24.
\]
With \(\xi\approx \sqrt{a_{\mathrm{cell}}}\,\ell_P\approx 1.28\,\ell_P\), the corresponding collar
benchmark is
\[
\delta_{\mathrm{CMB}}\approx 31\,\ell_P.
\]

\paragraph{\textbf{Theorem 6.3 (Homogeneity as the MaxEnt default).}}
If MaxEnt constraints are uniform across UV cells with no marked points, the MaxEnt state is
invariant under triangulation automorphisms. In the continuum limit this gives SO(3) invariance.

\paragraph{\textbf{Reading rule.}}
The cosmological-principle and horizon-homogeneity package is a conditional theorem package on the
realized symmetric MaxEnt branch. The exact theorem-level content is:
\begin{enumerate}[leftmargin=2em]
\item SO(3)-invariant constraint data plus MaxEnt uniqueness force an isotropic reference state and
      a perfect-fluid stress tensor.
\item If the same isotropy condition holds for all observers, the Schur/Bianchi argument forces
      constant-curvature spatial slices.
\item Combined with the semiclassical Einstein branch and positive \(\Lambda\) from finite screen
      capacity, the metric takes FLRW form.
\item Markov control supplies an explicit patch-overlap anisotropy bound and the collar benchmark
      used in the CMB homogeneity bookkeeping.
\end{enumerate}
The package does not prove from the bare OPH axioms alone that the realized cosmological branch
must satisfy SO(3)-invariant constraint data, that MaxEnt uniqueness holds in every cosmological
sector, or that the observed universe saturates the displayed CMB benchmark.

\subsection{Cosmological-Constant / Screen-Capacity Closure}

\paragraph{\textbf{Theorem 6.4 (D5--D6 local/global closure stack).}}
On the gravity lane, assume the local Einstein branch has been recovered only modulo
\(\Lambda g_{ab}\), the external input
\[
N_{\mathrm{scr}}=\log \dim \mathcal H_{\mathrm{tot}},
\]
the D6 screen-capacity identification
\[
N_{\mathrm{scr}}=S_{\mathrm{dS}},
\]
\noindent the standard de Sitter entropy relation
\[
S_{\mathrm{dS}}=\frac{A_{\mathrm{dS}}}{4G}=\frac{3\pi}{G\Lambda},
\]
and the standard de Sitter static-patch formulas
\[
r_{\mathrm{dS}}=\sqrt{\frac{3}{\Lambda}},
\qquad
t_\Lambda=\frac{r_{\mathrm{dS}}}{c}.
\]
Then:
\begin{enumerate}[leftmargin=2em]
\item local null data determine the Einstein branch only modulo \(\Lambda g_{ab}\);
\item the same branch closes globally as
\[
G_{ab}+\frac{3\pi}{G N_{\mathrm{scr}}}\,g_{ab}=8\pi G\,\langle T_{ab}\rangle;
\]
\item the same D6 closure fixes
\[
S_{\mathrm{dS}}=N_{\mathrm{scr}},
\qquad
A_{\mathrm{dS}}=4G N_{\mathrm{scr}},
\qquad
r_{\mathrm{dS}}=\sqrt{\frac{3}{\Lambda}},
\qquad
t_\Lambda=\frac{r_{\mathrm{dS}}}{c};
\]
\item the observed cosmic age remains a downstream FLRW benchmark rather than an additional theorem output.
\end{enumerate}
So the cosmological-constant package is one local/global theorem stack rather than a split local
argument plus an unrelated global readout.

\paragraph{\textbf{Scope boundary.}}
The imported premises are exactly the local Einstein branch, the external input
\(N_{\mathrm{scr}}\), the D6 identification \(N_{\mathrm{scr}}=S_{\mathrm{dS}}\), the de Sitter
entropy relation, and the standard static-patch formulas. What remains external is the
screen-capacity identification itself: the local null-data route does not derive
\(N_{\mathrm{scr}}=S_{\mathrm{dS}}\) from the bare OPH axioms.

\subsection{Black-Hole Structural Package and Continuation Boundary}

The AMPS-style information trilemma assumes:
\begin{enumerate}[leftmargin=2em]
\item an outgoing mode \(B\) entangled with an interior partner \(A\) (smooth horizon),
\item late radiation \(B\) entangled with early radiation \(R\) (unitarity), and
\item monogamy of entanglement.
\end{enumerate}
The false assumption in this setting is the naive tensor factorization
\[
\mathcal H \stackrel{?}{=}
\mathcal H_{\mathrm{inside}}\otimes
\mathcal H_{\mathrm{outside}}\otimes
\mathcal H_{\mathrm{radiation}}.
\]

\paragraph{\textbf{Theorem 7.1 (Edge-center black-hole decomposition).}}
On the fixed-cutoff edge-center collar branch, assume the black-hole collar state lies in the
exact Markov class or in the idealized exact-recoverability limit used elsewhere in the paper
stack. Then the collar decomposition gives
\[
\rho_{A_\delta B_\delta D_\delta}
=
\bigoplus_\alpha p_\alpha
\left(\rho_{A_\delta b_L^\alpha}\otimes \rho_{b_R^\alpha D_\delta}\right).
\]
The glue between inside and outside is the edge-sector label \(\alpha\) in the center.
Conditional on \(\alpha\), inside and outside factorize.

\paragraph{\textbf{Theorem 7.2 (Hawking/KMS normalization).}}
On the geometric modular branch where the horizon generator carries the standard \(2\pi\) KMS
normalization, the outside algebra is in a KMS state at inverse temperature
\[
\beta=\frac{2\pi}{\kappa}
\]
with respect to the horizon Killing generator.

\paragraph{\textbf{Corollary 7.3 (Recoverability-style interior encoding).}}
On the same fixed-cutoff collar carrier, when the collar conditional mutual information is small,
the interior partner is approximately
recoverable from outside plus radiation:
\[
\left\|
\rho_{ABC}
-
(\mathrm{id}_A\otimes\mathcal R)(\rho_{AB})
\right\|_1
\le
2\sqrt{\ln 2\cdot \varepsilon}.
\]
So the interior is encoded rather than supplied by an independent tensor factor.

\paragraph{\textbf{Corollary 7.4 (Discrete area spectrum and Schwarzschild transition identity).}}
The same edge-center package carries a discrete area operator
\[
L_C=\sum_\alpha (\log d_\alpha)P_\alpha,
\qquad
A_\alpha=4G\log d_\alpha=4\ell_P^2\ln d_\alpha,
\]
and for a Schwarzschild sector transition \(d\to d'\) one has
\[
\Delta E=k_B T_H\ln(d'/d).
\]

\paragraph{\textbf{Scope boundary.}}
The retained structural theorem package is exactly Theorem 7.1, Theorem 7.2, Corollary 7.3, and
Corollary 7.4. Integer-transition combs, QNM selectors, Page-type linewidth estimates, PBH burst
templates, Kerr/LIGO horizon spectroscopy templates, and any Page-curve or island closure remain
outside that structural core. Those items require extra premises such as an integer-transition
selection rule, a semiclassical evaporation-power model, a QNM/transition identification, greybody
matching, or an explicit island prescription.

\subsection{Modular-Anomaly Continuation}

\paragraph{\textbf{Theorem 9.1 (Modular additivity defect).}}
Define the collar modular additivity defect by
\[
\Delta K_\delta:=K_{ABD}-K_{AB}-K_{BD}+K_B.
\]
Then
\[
\langle \Delta K_\delta\rangle_\omega=-I(A:D\mid B)_\omega.
\]
This is the precise structural identity underneath the modular-anomaly dark-sector continuation. By itself it does not close a dark-matter theorem.

The corresponding continuation packages the anomalous contribution into the modified Einstein
equation
\[
G_{ab}+\Lambda g_{ab}
=
8\pi G\left(\langle T_{ab}\rangle+\langle T_{ab}^{\mathrm{anom}}\rangle\right),
\]
with rest-frame normalization
\[
\langle T_{00}^{\mathrm{anom}}\rangle
:=
\frac{15}{8\pi^2}\,
\frac{\delta\langle K_C^{\mathrm{anom}}\rangle}{\ell^4}.
\]
On that continuation surface the anomaly gravitates, is dark by construction, is covariantly
conserved, and is effectively classical because it is organized by central/recoverability data.

If one tentatively identifies the imported D6 static-patch radius \(r_{\mathrm{dS}}\) as the
unique IR scale available to the continuation, the natural benchmark acceleration is
\[
a_0^{(\mathrm{OPH})}
:=
\frac{15}{8\pi^2}c^2\sqrt{\frac{\Lambda}{3}}
=
\frac{15}{8\pi^2}\frac{c^2}{r_{\mathrm{dS}}}
\approx
1.03\times 10^{-10}\ \mathrm{m/s^2},
\]
close to the empirical MOND scale. That numerical proximity is only a benchmark unless a separate
source/response law and a controlled galaxy-scale limit are derived. An illustrative MOND/RAR-style response would read
\[
g_{\mathrm{obs}}\approx g_b+\sqrt{a_0 g_b},
\]
but that functional form is not derived from the OPH axioms.

\paragraph{\textbf{Reading rule.}}
The anomaly term gravitates, is dark by construction, and is covariantly conserved, but the live
synthesis surface keeps the entire dark-sector package on the D12 continuation tier rather than
promoting any MOND/RAR-style law, galaxy-rotation template, or cluster phenomenology to theorem
status. The imported D6 static-patch scale fixes only the benchmark normalization. The missing
inputs are the controlled nonrelativistic limit, derived sign and closure control for the
effective anomaly contribution, a derived source/response law, proof of the relevant dominant
galaxy-scale source, lensing and cluster phenomenology, cosmological abundance and
structure-formation checks, and environment/stability bounds. Those remain continuation-level
branches above the identity written here.
