\section{Candidate Microphysics Reference Architecture}

The synthesis paper keeps the observer-facing theorem package in the main text, but the concrete
finite screen architecture belongs in an appendix. The current theorem-bearing fixed-cutoff
source surface for the edge heat-kernel / Casimir leaf is the microphysics side paper; the
appendix records only the synthesis-level restatement imported from that surface. The working OPH
reference architecture is a finite cellulation of the horizon screen with boundary-fixed patch
algebras, boundary-fixed overlap algebras on collars, declared shared readout packets, local
repair instruments, and record registers exposed on the observer-facing interface.

\paragraph{Theorem (Regulated patch-net embedding).}
On a fixed finite cellulation and finite patch cover, the regulated OPH microphysics realizes an
explicit finite patch-net layer: patch vertices are genuine screen patches, overlap edges are
genuine collars, packet fields are actual readouts of declared overlap observables, and allowed
repair branches are concrete local channels on the same finite regulator.

\paragraph{Proof sketch.}
All patch and overlap algebras are finite-dimensional at fixed cutoff, and the declared packet
fields are readouts of explicit overlap observables in those algebras. The candidate repair menu
is implemented by local finite-support channels on the same neighborhoods. Therefore the abstract
finite patch-net syntax is embedded into an explicit regulator object rather than introduced as a
separate formal layer.

\paragraph{Theorem (Fixed-cutoff edge heat-kernel branch).}
On the thermalized overlap branch of the same regulated architecture, the stationary sector law is
\[
\pi_\beta(\alpha)\propto d_\alpha e^{-\beta C_2(\alpha)},
\]
and along refinement ladders converging to a compact-group Peter--Weyl decomposition~\cite{peterWeyl27} the same
weights converge cylinderwise to the heat-kernel/Casimir law used in the OPH edge-sector branch.

\paragraph{Proof sketch.}
The regulated proposal kernel is chosen so that the weighted proposal symmetry
\(d_\alpha q_{\alpha\beta}=d_\beta q_{\beta\alpha}\) holds. Detailed balance with the Casimir
acceptance rule then fixes the stationary distribution in finite dimension, and the compact-group
heat-kernel law is the corresponding refinement lift.

\paragraph{Extended derivation.}
The full fixed-cutoff architecture, validation package, and theorem stacks are developed in
\emph{Screen Microphysics, Patches, and Observer Synchronization in OPH}~\cite{ophmicrophysics}.

\section{Interpretive Epilogue: Habitat and Strange-Loop Closure}

This appendix is interpretive. It uses the OPH state-and-law habitat theorem and leaves the
closure map on an observer-supporting sector open.

The OPH inputs used here are:
\begin{enumerate}
\item the patch net \(P\mapsto A(P)\) of von Neumann algebras together with isotony and overlap
restriction maps;
\item the global state on the inductive-limit algebra, whose restrictions witness a nonempty
overlap-consistent local sector;
\item the finite Axiom-3 MaxEnt/refinement branch, which supplies a common finite family of
gauge-invariant local constraint observables across cutoffs;
\item on the fixed-cutoff branch, the derived finite type-I presentations and compact boundary
gluing groups used elsewhere in the OPH package.
\end{enumerate}

The law slot is encoded by the finite expectation-value coordinates of the retained Axiom-3
constraint family. That choice furnishes a compact convex state-and-law habitat within OPH.

\paragraph{Theorem (OPH internal state-and-law habitat theorem).}
Fix finitely many screen patches \(P_1,\dots,P_N\) in the standard OPH setup. For each \(i\), let
\[
M_i:=A(P_i),
\qquad
M_{ij}:=A(P_i\cap P_j),
\]
where \(M_i\) is the patch von Neumann algebra and \(M_{ij}\subset M_i,M_j\) is the overlap
algebra. Let
\[
S_i:=S(M_i)\subset M_i^*
\]
be the full state space of \(M_i\), endowed with the weak* topology \(\sigma(M_i^*,M_i)\).

Choose a finite family of self-adjoint gauge-invariant local constraint observables
\[
\mathcal O=\{O_1,\dots,O_m\}
\]
from the Axiom-3 MaxEnt branch, with each \(O_a\) supported in one of the chosen patches; write
\(i(a)\) for an index such that \(O_a\in M_{i(a)}\).

Define the overlap-consistent state sector
\[
X_{\mathrm{ov}}
:=
\left\{
(\omega_1,\dots,\omega_N)\in \prod_{i=1}^N S_i:
\omega_i|_{M_{ij}}=\omega_j|_{M_{ij}}\ \text{for all }i,j
\right\}.
\]
Define the OPH law-coordinate map
\[
c:X_{\mathrm{ov}}\to \mathbb R^m,
\qquad
c(\omega_1,\dots,\omega_N)
:=
\bigl(\omega_{i(1)}(O_1),\dots,\omega_{i(m)}(O_m)\bigr).
\]
Let
\[
X_{\mathcal O}
:=
\left\{
(\omega_1,\dots,\omega_N,\ell)\in
\left(\prod_{i=1}^N S_i\right)\times \mathbb R^m:
(\omega_1,\dots,\omega_N)\in X_{\mathrm{ov}},
\ \ell=c(\omega_1,\dots,\omega_N)
\right\}.
\]
Then:
\begin{enumerate}
\item the ambient product
\[
E:=
\left(\prod_{i=1}^N M_i^*\right)\times \mathbb R^m
\]
is a Banach space for any product norm;
\item \(X_{\mathcal O}\) is nonempty and convex;
\item \(X_{\mathcal O}\) is norm-closed in \(E\);
\item \(X_{\mathcal O}\) is compact in the product topology
\[
\tau
:=
\left(\prod_{i=1}^N \sigma(M_i^*,M_i)\right)\times
\text{Euclidean topology on }\mathbb R^m;
\]
\item therefore every \(\tau\)-continuous self-map
\[
\Phi:X_{\mathcal O}\to X_{\mathcal O}
\]
has a fixed point.
\end{enumerate}

\begin{proof}
Each \(M_i\) is a von Neumann algebra in the OPH patch net, hence a Banach space, so each dual
\(M_i^*\) is Banach. A finite product of Banach spaces is Banach, hence so is \(E\).

For each \(i\), the state space
\[
S_i=\{\omega\in M_i^*:\omega\ge 0,\ \omega(1)=1\}
\]
is convex and weak* compact by Banach--Alaoglu, because it is a weak* closed subset of the dual
unit ball. For every pair \((i,j)\), restriction along \(M_{ij}\subset M_i\) and
\(M_{ij}\subset M_j\) defines affine weak* continuous maps
\[
r_{ij}:S_i\to S(M_{ij}),
\qquad
r_{ji}:S_j\to S(M_{ij}).
\]
Hence \(X_{\mathrm{ov}}\) is an intersection of affine equalizer sets, so it is convex and
\(\tau\)-closed inside \(\prod_i S_i\). Since \(\prod_i S_i\) is compact and convex in the
product weak* topology, \(X_{\mathrm{ov}}\) is compact and convex as well.

Nonemptiness comes from the OPH global state on the inductive-limit algebra: its restrictions
\[
\bigl(\omega|_{M_1},\dots,\omega|_{M_N}\bigr)
\]
belong to \(X_{\mathrm{ov}}\) because the restrictions agree on every overlap by construction.

Each coordinate \(\omega_{i(a)}\mapsto \omega_{i(a)}(O_a)\) is affine and weak* continuous, since
evaluation at a fixed algebra element is weak* continuous. Thus \(c\) is affine and
\(\tau\)-continuous. The graph map
\[
G:X_{\mathrm{ov}}\to E,
\qquad
G(x):=(x,c(x)),
\]
is affine and continuous, so its image \(X_{\mathcal O}=G(X_{\mathrm{ov}})\) is convex and
\(\tau\)-compact.

To see norm-closedness in \(E\), let \((x_n,c(x_n))\to (x,\ell)\) in norm. Norm convergence
implies weak* convergence on each coordinate, so \(x\in X_{\mathrm{ov}}\) because
\(X_{\mathrm{ov}}\) is weak* closed. Since \(c\) is weak* continuous, \(c(x_n)\to c(x)\), while
norm convergence in \(\mathbb R^m\) also gives \(c(x_n)\to \ell\). Hence \(\ell=c(x)\), so
\((x,\ell)\in X_{\mathcal O}\).

Finally, \(X_{\mathcal O}\) is a compact convex subset of the locally convex topological vector
space \(E\) equipped with \(\tau\). Therefore every \(\tau\)-continuous self-map
\(\Phi:X_{\mathcal O}\to X_{\mathcal O}\) has a fixed point by the Schauder--Tychonoff
fixed-point theorem.
\end{proof}

\paragraph{Corollary (Fixed-cutoff OPH Brouwer corollary).}
On the fixed-cutoff realized presentation of OPH, each chosen patch algebra \(M_i=A(P_i)\) is
finite-dimensional. Then \(E\) is finite-dimensional, the weak* and norm topologies coincide on
\(E\), and \(X_{\mathcal O}\) is a nonempty compact convex subset of a finite-dimensional real
vector space. Hence every continuous self-map
\[
\Phi:X_{\mathcal O}\to X_{\mathcal O}
\]
has a fixed point by Brouwer. If, moreover, \(\Phi\) is a contraction for some metric on
\(X_{\mathcal O}\), then the fixed point is unique and the iterates converge to it from every
starting point by Banach's contraction theorem.

\begin{proof}
On that fixed-cutoff realized presentation, each chosen patch algebra is identified
with a finite-dimensional type-I presentation modulo compact boundary redundancy, so each \(M_i\)
and \(M_i^*\) is finite-dimensional. Hence \(E\) is finite-dimensional and all relevant locally
convex topologies coincide. The habitat theorem above shows that \(X_{\mathcal O}\) is nonempty,
compact, and convex, so Brouwer gives a fixed point for every continuous self-map. The
contraction statement is the usual Banach fixed-point theorem.
\end{proof}

The additional inputs needed for a strange-loop closure theorem are:
\begin{enumerate}
\item an actual OPH closure map \(\Phi\) built from internal operations such as overlap repair,
Axiom-3 MaxEnt reprojection, collar recoverability, and record-sector coarse-graining;
\item a proof that the stronger ``observer-supporting'' or ``selected-world'' criteria carve out a
nonempty compact convex \(\Phi\)-invariant subset of \(X_{\mathcal O}\);
\item any uniqueness, contraction, or Lyapunov-type stability estimate for that closure map.
\end{enumerate}

The habitat theorem supplies the Banach/compact-convex setting. A strange-loop closure theorem
would additionally require the closure map and the stronger invariant-sector and stability
inputs.

\subsection{Timeless Causal Chain}

The hypothesis is represented by the chain
\[
\begin{aligned}
\text{information constraints}
&\to \text{effective physics}
\to \text{complex chemistry and biology}\\
&\to \text{observers with records}
\to \text{formal OPH reconstruction}\\
&\to \text{OPH-compatible simulation substrate}
\to \text{information constraints}.
\end{aligned}
\]
In this appendix the chain is interpreted as a consistency loop. The discussion does not use it as
a linear first-cause narrative. The Escher drawing-hands image is used only as a geometric
analogy for this closure structure.

\subsection{Why Reality Exists and Why It Has This Form}

Under this hypothesis, existence is identified with nontrivial fixed points of the OPH
consistency map. The observed form of reality is selected by stability requirements:
\begin{enumerate}
\item overlap-consistent sharable records,
\item recoverability under local information loss,
\item long-lived structured sectors that support observer formation,
\item internal reconstructibility of the governing rule set.
\end{enumerate}
The appearance of intelligent observers enters the closure mechanism itself. Observer-capable
worlds are the sectors that complete the loop.

\subsection{Additional Problem Closures}

Using the documentary node labels defined in Section~\ref{16-summary-complete-axiom-set}, Phase I
is D1--D5 together with D7--D9; D6 is the separate input-dependent corollary; and D12
collects phenomenological continuations. Ref.~\cite{ophmicrophysics} proves fixed-cutoff theorem
packages for the measurement/Born-rule interface and for checkpoint/restoration/backup.
Table~\ref{tab:additional-closures} records the status of the broader problem-closure claims
discussed in the OPH synthesis surfaces.

\begin{longtable}{p{0.24\textwidth} p{0.19\textwidth} p{0.50\textwidth}}
\caption{Problem-closure statements sorted by claim tier.}\label{tab:additional-closures}\\
\toprule
Problem domain & Status & OPH mechanism / scope note \\
\midrule
\endfirsthead
\toprule
Problem domain & Status & OPH mechanism / scope note \\
\midrule
\endhead
\bottomrule
\endfoot
Quantum gravity consistency & Phase I recovered core (conditional scaling-limit) & Conditional Lorentz and Jacobson-type Einstein branches from modular geometry, the null bridge, and fixed-cap stationarity. \\
UV completion / microscopic uniqueness & Mixed: fixed-cutoff theorem package / conditional scaling-limit branch & OPH gives a finite-range interacting fixed-cutoff branch, a unique physical UV branch only modulo OPH-stable equivalence, and a fixed-cutoff higher-gauge closure of the genuinely noncentral topological branch. Open items are a unique microscopic representative, the continuum BW lift on the extracted geometric subnet behind T2 plus cap-pair extraction and ordered cut-pair rigidity, and the refinement-limit transportable compact-gauge lift behind T1/T4--T6. \\
Measurement problem & Mixed: fixed-cutoff theorem package / interpretive synthesis & Ref.~\cite{ophmicrophysics} proves a fixed-cutoff central-record / Born-Luders package for observer-accessible events. Broader philosophical closure claims remain interpretive here. \\
Cosmological principle and horizon homogeneity & Interpretive or organizational synthesis & MaxEnt state selection under symmetric constraints motivates isotropy and homogeneity stories. Those stories remain outside the independent Phase-I theorems. \\
Problem of time & Interpretive or organizational synthesis & Modular flow from the BW\(_{S^2}\) geometric branch provides a physical time parameter for each observer patch. It is an organizational principle rather than a separate recovered-core theorem. \\
Black-hole information paradox & Phenomenological continuation & Edge-center sectorization and recoverability suggest an internal resolution. The full black-hole-information branch remains outside Phase I. \\
Cosmological constant problem & Phase II input-dependent corollary & \(\Lambda\) is tied to global screen capacity once the screen-capacity identification is adopted. This sits outside the local recovered-core outputs. \\
Magnetic monopole expectation from simple GUT groups & Phase I recovered core & The realized product-group branch \(\SU(3)\times\SU(2)\times\U(1)/\mathbb Z_6\) removes the standard simple-GUT symmetry-breaking monopole channel. \\
Proton stability and proton spin fraction & Mixed: Phase I / Phase III & No gauge-mediated proton decay follows from the realized product-group branch, which removes the standard simple-GUT proton-decay channel. Proton spin requires nonperturbative QCD completion and is not part of Phase I. \\
Dark matter phenomenology & Phase III deferred continuation & Modular-anomaly response laws remain conjectural beyond the recovered gravity chain. \\
Baryon asymmetry scale & Phase III deferred continuation & Suppression-counting estimates are not a substitute for a derived out-of-equilibrium mechanism. \\
Three generations and downstream flavor structure & Mixed: Phase I / Phase III & \(N_g=3\) is recovered on the realized MAR-admissible branch; later flavor constructions require extra ansatze. \\
String/worldsheet reorganization & Phase III deferred continuation & Requires a controlled large-\(N_{\mathrm{edge}}\) regime distinct from the physical color rank \(N_c=3\). Any further lift to critical superstring structure remains a conjectural extension requiring extra worldsheet ingredients not derived in the OPH core. \\
Why anything exists / strange-loop closure & Interpretive epilogue only & Appendix B gives an OPH-internal state-and-law habitat theorem: overlap-consistent patch states together with finite Axiom-3 law coordinates form a theorem-usable nonempty compact convex sector, and fixed-cutoff branches admit a Brouwer version. Additional inputs are the OPH closure map on an invariant observer-supporting sector, together with uniqueness and stability. \\
\end{longtable}

\section{Observer Continuation and Backup}

This appendix uses the fixed-cutoff checkpoint/restoration/error/identity theorem package proved
in Ref.~\cite{ophmicrophysics} and summarizes its algebraic interface in observer language. It
does not define a strange-loop closure map on an invariant observer-supporting sector or establish
uniqueness and stability for such a map.

\subsection{Observer as Algebraic Pattern}

Here, an observer is represented by
\[
O=(P,\mathcal{A}(P),\rho,R),
\]
where \(P\) is a screen patch, \(\mathcal{A}(P)\) is its local algebra, \(\rho\) is the local
state, and \(R\) is the record algebra. Records are implemented by approximately commuting
projectors in overlap centers, so they are shareable without violating no-cloning constraints for
generic quantum states.

Ref.~\cite{ophmicrophysics} proves a fixed-cutoff observer-facing measurement interface: a
finite central record algebra, Born probabilities for its event projectors, and Luders
conditioning on that same commuting record algebra. This appendix uses that fixed-cutoff
measurement package in observer language.

\subsection{Markov Collar Factorization}

For a collar tripartition \(A\)-\(B\)-\(D\) with conditional mutual information
\(I(A:D|B)\le\varepsilon\), the exact Markov limit gives
\[
\rho_{ABD}
=\bigoplus_{\alpha} p_{\alpha}\,
\rho^{(\alpha)}_{A b_L^{\alpha}}
\otimes
\rho^{(\alpha)}_{b_R^{\alpha} D}.
\]
The sector label \(\alpha\) is classical center data. This decomposition is the mathematical
basis for extracting an interior observer state with a controlled boundary interface.

\subsection{Checkpoint and Restoration Map}

A checkpoint is the tuple
\[
\mathcal{C}=\bigl(R,\alpha,\rho_{\mathrm{int}}^{(\alpha)}\bigr),
\]
with \(\rho_{\mathrm{int}}^{(\alpha)}\) the interior conditional state. Given a compatible target
environment state \(\sigma_{\mathrm{env}}^{(\alpha)}\), a restored state is
\[
\rho_{\mathrm{new}}^{(\alpha)}
=
\rho_{\mathrm{int}}^{(\alpha)}
\otimes
\sigma_{\mathrm{env}}^{(\alpha)}.
\]
For approximate Markov collars, recovery is controlled by the standard bound
\[
\left\|
\rho_{ABD}
-
(\mathrm{id}_A\otimes\mathcal{R}_{B\to BD})(\rho_{AB})
\right\|_1
\le
2\sqrt{\ln 2\,\varepsilon}.
\]
This gives quantitative trace-distance control on the recovered state under finite conditional
mutual information (finite collar error). Interpreting that control as observer continuation
requires additional modeling assumptions beyond the bound itself.

The fixed-cutoff microphysics claim is stronger than the bare recoverability estimate written
above. In Ref.~\cite{ophmicrophysics}, exact checkpoint restoration preserves the full future
law of observer-accessible events, while an \(\varepsilon\)-accurate restoration changes that
future law by at most \(\varepsilon\) in total variation. The stronger strange-loop closure story
remains open.

\subsection{Physical Meaning}

At fixed cutoff, Ref.~\cite{ophmicrophysics} proves a checkpoint/restoration theorem and backup
corollary for observer-accessible event algebras. This appendix states the observer-facing meaning
of that theorem and its algebraic prerequisites. Open items are the stronger substrate-selection,
strange-loop closure, uniqueness, and stability package.

\input{tex_fragments/OBSERVERS_TECHNICAL_SUPPLEMENT_PORT.tex}
