\section{Consensus, Defects, and Implementation Hiding}

The fixed-cutoff consensus package admits an equivalent finite patch-net formulation. Local patch descriptions agree on
overlaps, local recovery-derived repair rules remove mismatches, and the physical output is the
schedule-independent quotient normal form together with the induced terminal expectation
functionals on the declared physical observable algebras. This section records the fixed-point,
defect, and gauge-quotient statements in that language.

The consensus lane also carries a simple finite-candidate law-selection model: once one equips
candidate repair rules with a fitness functional, replicator dynamics gives a clean toy picture in
which more successful reconciliation laws dominate a competing pool. That selection picture is
useful for the overall synthesis picture, but in the consensus paper it remains a finite-candidate
monotonicity result, not part of the recovered-core gravity/gauge theorem surface, not a
universality claim, and not a literal cosmological dynamics claim.

On its declared fixed-cutoff branch, \emph{Reality as a Consensus Protocol: The Fixed-Point
Computation That Implements Physics}~\cite{ophconsensus} imports four core D1 surfaces into the
wrapper:
\begin{enumerate}[leftmargin=2em]
\item \textbf{Asynchronous confluence.} For the declared accepted repair law, the local-fit
contract makes \(\Phi\) a Lyapunov functional and, together with the fixed-cutoff union-collar
gluing package, yields a unique schedule-independent normal form under repair completeness.
\item \textbf{Cycle obstruction and higher-gauge defects.} On the abelian branch, global
consistency holds exactly when cycle holonomy vanishes; on the genuinely noncentral branch, the
crossed-module defect class
\[
q_\Sigma \in \check H^2(N_\Sigma,H_\Sigma \to G_\Sigma)
\]
labels the fixed-cutoff higher-gauge obstruction.
\item \textbf{Gauge quotient and observable-level confluence.} The repair law descends to the
overlap-invariant quotient, and the induced terminal state on the declared physical observable
algebras is unique there even when microscopic representatives differ by gauge or sector
relabelings inside one quotient-local glued state.
\item \textbf{Record algebra and stability.} On the fixed-cutoff observer-accessible surface,
central record projectors carry the Born/L\"uders package directly, while approximate record
projectors inherit explicit \((\varepsilon,\delta_{\mathrm{rec}})\) stability bounds on that same
event surface.
\end{enumerate}

The consensus paper is equally explicit about the imported repair-law data and what remains
outside the fixed-cutoff theorem stack. The declared repair step already includes the
touched-overlap local-fit contract and the union-collar gluing package on the physical quotient;
the remaining burdens above that step are repair completeness and, on the Petz branch, the stated
support/CPTP clause. On that same fixed-cutoff surface, exact normal-form computation is
finite-state and decidable, approximate stability is only collar-local through the splice and
record estimates, no global approximate-consensus theorem for long asynchronous noisy repair is
claimed, and no universality theorem for a uniform family of growing patch nets and repair laws is
claimed.

\section{Particle-Spectrum Branch}

The particle branch follows the same logical order as
\emph{Deriving the Particle Zoo from Observer Consistency}~\cite{ophparticles}.
One first fixes the compact-gauge basis and realized branch, then identifies the realized
Standard Model quotient, and only then asks how transport-stable overlap data organize the
observed particle families.

\paragraph{Structural particle theorem package.}
On the realized compact-gauge branch, the structural carrier skeleton is fixed by the compact
gauge and MAR-admissibility chain:
\[
\frac{\SU(3)\times\SU(2)\times\U(1)}{\mathbb Z_6},
\qquad
N_g=3,
\qquad
N_c=3.
\]
This determines the exact structural zero rows carried by the gauge and gravity sectors:
the photon, gluons, and graviton are massless structural carriers on the realized branch.

\paragraph{Proof route.}
The proof route is the one developed in
\emph{Recovering Relativity and the Standard Model from the OPH Package Rooted in Observer Consistency}~\cite{ophcompact}
and
\emph{Deriving the Particle Zoo from Observer Consistency}~\cite{ophparticles}.
Under the explicit transportable-colimit, symmetry, and bosonic fiber-functor premises of the
compact paper, the surviving transportable edge-sector category reconstructs a compact internal
symmetry group. MAR then selects the realized admissible branch, anomaly freedom
fixes the hypercharge lattice, and the realized one-generation/one-Higgs package forces \(N_g=3\)
and then \(N_c=3\). The particle branch builds on that structural skeleton and does not bypass
it.

\scriptsize
\setlength{\tabcolsep}{2pt}
\begin{longtable}{@{}>{\raggedright\arraybackslash}p{0.175\textwidth}>{\raggedright\arraybackslash}p{0.165\textwidth}>{\raggedright\arraybackslash}p{0.225\textwidth}>{\raggedright\arraybackslash}p{0.325\textwidth}@{}}
\toprule
Sector & Claim tier & What is fixed here & Boundary to stronger claim \\
\midrule
\endfirsthead
\toprule
Sector & Claim tier & What is fixed here & Boundary to stronger claim \\
\midrule
\endhead
\bottomrule
\endfoot
Structural carriers & realized-branch structural theorem & exact \(m_\gamma=m_g=m_{\mathrm{grav}}=0\); realized quotient; \(N_g=3\); \(N_c=3\) & theorem-grade structural exactness on the particle side \\
Electroweak bosons & quantitative-closure branch + exact sidecar & target-free public \(W/Z\) rows together with the exact frozen-repair pair \(M_W=80.377~\mathrm{GeV}\), \(M_Z=91.18797809193725~\mathrm{GeV}\) & exact only on the frozen authoritative repair surface; the public theorem rows remain the target-free electroweak outputs \\
Higgs/top stage & exact source-only D11 split theorem on the declared D10/D11 running, matching, and threshold surface + compare-only exact sidecar & shared scalar \(\rho_{HT}\), source-only split selectors, and the declared D11 Jacobian together with an exact Higgs/top inverse pair & the split theorem is closed on the declared quantitative surface; the inverse pair is compare-only and does not replace the theorem rows \\
Quark family & selected-class theorem + exact supporting surfaces & exact running quark sextet together with explicit exact forward Yukawas on the public physical quark frame class \(f_P\) & selected-class closure only; the sextet matches the official PDG 2025 API running-quark surface exactly, with the top coordinate taken from the PDG cross-section entry; supporting exact surfaces are the same-family witness on \texttt{current\_family\_only} and the restricted common-refinement transport-frame exact chain, which also emits explicit exact forward Yukawas \(Y_u\) and \(Y_d\); the target-free mass bridge \(\Theta_{ud}^{\mathrm{mass}}=\text{\ophid{quark_d12_t1_value_law}}\) closes separately on the emitted D12 mass ray; \(\sigma_{\mathrm{ref}}\) is a lower negative sheet statement beneath the selected-class theorem; no global classification of all quark frame classes is claimed; a stronger class-uniform public descent theorem is separate and is not claimed \\
Charged leptons & continuation branch + exact witness & exact same-family charged triple plus exact same-carrier centered readback, with the ordered three-point quadratic readout closed on that scope & same-family-only on the exact witness; theorem lane carries the closed common-shift no-go, then waits on \(\widehat C_e^{\mathrm{cand}}\) and the post-promotion lift whose descended scalar is \(\mu_{\mathrm{phys}}(Y_e)\), with the physical identity-mode equalizer beneath that scalar \\
Neutrinos & weighted-cycle continuation + emitted bridge invariant + diagnostic sidecars & emitted absolute masses/splittings on the weighted-cycle branch through the bridge-rigidity invariant \(C_\nu=G^2Q S^{-1/2}\) above the emitted proxy \(P_\nu\), with induced paper-facing amplitude \(B_\nu\) & theorem-grade on the declared weighted-cycle branch; the exact positive-segment adapter, bridge corridor, and correction audit remain diagnostic-only and do not feed back into theorem state \\
Hadrons & nonperturbative continuation & stable-channel and readout architecture are defined & one production backend export bundle, then executed unquenching, runtime receipt, and production systematics \\
\end{longtable}
\normalsize

\paragraph{Claim-tier boundary.}
Structural carrier content and the realized Standard Model branch are theorem-bearing outputs.
The electroweak D10 branch, the Higgs/top stage, quark rows, charged-lepton rows, neutrino rows, and
hadron rows sit on their stated quantitative-closure, continuation, or nonperturbative claim tiers.
On the target-free electroweak D10 lane, the logical order is forward: the outer/inner closure relation fixes \(P\), and then \(P\) fixes \(\alpha_U(P)\),
equivalently \(t_U(P)\) and \(t_{\mathrm{tr}}(P)\), then the downstream scale data and public
electroweak rows. Measured electroweak quantities remain compare-only validation targets and do
not feed back into the transmutation solve.

\paragraph{Outer/inner self-consistency for the pixel ratio.}\label{sec:p-closure}
This synthesis paper is the canonical place where the local pixel ratio \(P\) is defined, so the
compact and particle papers can cite one derivation rather than duplicate it. The construction has
five steps.
\begin{enumerate}[leftmargin=2em]
\item \textbf{Outer pixel ratio.} The simulator-side local screen datum is the dimensionless area
ratio
\[
P:=\frac{a_{\mathrm{cell}}}{\ell_P^2}.
\]
\item \textbf{Exact equilibrium benchmark.} The total/bulk/edge hierarchy has one exact
self-similar balance point. Writing
\[
x(C):=\frac{S_{\mathrm{gen}}(C)}{S_{\mathrm{bulk}}(C)}
=
1+\frac{\langle L_C\rangle}{S_{\mathrm{bulk}}(C)},
\]
the self-similar balance condition
\[
\frac{S_{\mathrm{gen}}(C)}{S_{\mathrm{bulk}}(C)}
=
\frac{S_{\mathrm{bulk}}(C)}{\langle L_C\rangle}
\]
gives \(x^2-x-1=0\) and hence \(x=\varphi=(1+\sqrt5)/2\). The realized branch must sit near, but
not exactly at, this point because exact equilibrium is too symmetric to support durable records,
structure, and dynamics.
\item \textbf{Outer detuning variable.} We therefore write the simulator-side detuning as
\[
\alpha_{\mathrm{ext}}(P):=\frac{P-\varphi}{\sqrt{\pi}},
\qquad\text{equivalently}\qquad
P=\varphi+\alpha_{\mathrm{ext}}(P)\sqrt{\pi}.
\]
\item \textbf{Inner observation scale from the same pixel.} For any trial \(P\), the forward D10
lane emits the inner electroweak/electromagnetic hierarchy
\[
P\longmapsto \alpha_U(P)\longmapsto (t_U(P),t_{\mathrm{tr}}(P))
\longmapsto (t_2(P),t_3(P),v(P))
\longmapsto a_0(P)=\alpha_{\mathrm{em}}^{-1}(m_Z^2;P).
\]
On the chosen electromagnetic transport lane, write \(\alpha_{\mathrm{in}}(P)\) for the
corresponding inner coupling scale carried by that same forward branch. On the paper surface, the
most source-local inner quantity is the anchor \(a_0(P)\); later Ward-projected low-energy
descendants sit below that same emitted map.
\item \textbf{Closure.} The realized pixel ratio is the fixed point for which the outer detuning
equals the inner observation coupling:
\[
\alpha_{\mathrm{ext}}(P)=\alpha_{\mathrm{in}}(P).
\]
Equivalently,
\[
P=\varphi+\alpha_{\mathrm{in}}(P)\sqrt{\pi}.
\]
\end{enumerate}
Writing
\[
g(P):=\varphi+\alpha_{\mathrm{in}}(P)\sqrt{\pi},
\]
the closure problem is the fixed-point condition \(g(P)=P\). On any physical interval where this
induced map is a self-map and a contraction, the closure root is locally unique.

Informally, the same screen cell must do two jobs at once. On the outer side it is a finite pixel
of the simulating screen. On the inner side it is the source of the smallest electromagnetic
observation step available to observers in the simulated world. The fixed-point equation is
therefore the statement that these two descriptions of the same cell agree. Once the fixed point
\(P_\star\) is selected, every downstream D10/D11 quantity is propagated forward from that same
\(P_\star\); it is not separately fitted sector by sector.

\paragraph{Exact non-hadron hit surface.}
For quick orientation, the exact non-hadron lanes are:

\begin{table}[h]
\centering
\scriptsize
\setlength{\tabcolsep}{3pt}
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.14\textwidth}>{\raggedright\arraybackslash}p{0.17\textwidth}>{\raggedright\arraybackslash}p{0.31\textwidth}>{\raggedright\arraybackslash}p{0.30\textwidth}@{}}
\toprule
Lane & Exact output(s) & Exact OPH chain on the paper surface & Caveat \\
\midrule
Structural carriers & \(m_\gamma=m_g=m_{\mathrm{grav}}=0\) & axioms \(\rightarrow\) realized electromagnetic/color/dynamical-metric carrier skeleton \(\rightarrow\) symmetry-protected zeros & theorem-grade structural exactness \\
Electroweak exact sidecar & exact frozen \(W/Z\) pair & axioms \(\rightarrow\) gauge reconstruction \(\rightarrow\) target-free electroweak quantitative-closure solve \(\rightarrow\) exact frozen repair pair & exact only on the frozen authoritative repair surface; compare-only beneath the target-free theorem \\
Higgs/top exact sidecar & exact Higgs/top inverse pair & axioms \(\rightarrow\) electroweak core \(\rightarrow\) D11 Jacobian \(\rightarrow\) exact inverse slice & compare-only inverse slice; the public Higgs/top pair comes from the source-only split theorem on the declared surface, while the repo-wide exact public top row is also carried by the selected-class quark theorem \\
Charged exact witness & exact same-family charged triple & axioms \(\rightarrow\) shared excitation dictionary \(\rightarrow\) ordered charged carrier \(\rightarrow\) exact centered readback \(\rightarrow\) closed quadratic readout theorem \(\rightarrow\) same-family exact witness & same-family-only; theorem lane carries exact centered readback plus the closed common-shift no-go, then waits on \(\widehat C_e^{\mathrm{cand}}\) and the post-promotion lift whose descended scalar is \(\mu_{\mathrm{phys}}(Y_e)\), with the physical identity-mode equalizer beneath that scalar \\
Quark selected-class theorem & exact running quark sextet plus explicit exact forward Yukawas on \(f_P\) & axioms \(\rightarrow\) shared excitation dictionary \(\rightarrow\) D12 mass bridge \(\rightarrow\) selected public quark frame class \(f_P\) \(\rightarrow\) direct public sigma-datum descent \(\rightarrow\) affine mean law \(\rightarrow\) ordered three-point readout \(\rightarrow\) exact forward construction & selected-class closure on the public physical quark frame class chosen by \(P\); the sextet matches the official PDG 2025 API running-quark surface exactly, with the top coordinate taken from the PDG cross-section entry; the bridge to the auxiliary direct-top PDG row remains open and is tracked in \href{https://github.com/FloatingPragma/observer-patch-holography/issues/207}{issue \#207}; the same exact sextet is also realized by the same-family witness on \texttt{current\_family\_only} and by the restricted common-refinement transport-frame exact chain, which also carries explicit exact forward Yukawas \(Y_u\) and \(Y_d\); the target-free mass bridge \(\Delta_{ud}^{\mathrm{overlap}}=\tfrac16\log(c_d/c_u)\), equivalently \(\Theta_{ud}^{\mathrm{mass}}=\text{\ophid{quark_d12_t1_value_law}}\), closes separately on the emitted D12 mass ray; the historical selector \(\sigma_{\mathrm{ref}}\) is a lower negative sheet statement beneath the selected-class theorem; no global classification of all quark frame classes is claimed; a stronger class-uniform public descent theorem is separate and is not claimed \\
Neutrino theorem branch & emitted absolute mass triple and representative central splittings & axioms \(\rightarrow\) same-label scalar certificate \(\rightarrow\) weighted-cycle branch \(\rightarrow\) bridge-rigidity theorem \(\rightarrow\) absolute-attachment theorem & theorem-grade on the declared weighted-cycle branch; the positive-segment adapter, bridge corridor, and bridge-coordinate sidecars remain diagnostic-only \\
\bottomrule
\end{tabular}
\end{table}

\noindent The explicit values behind these exact-hit lanes are the exact frozen
\(W/Z\) pair, the exact Higgs/top inverse pair, the exact same-family charged triple,
the exact same-family quark sextet, and the emitted weighted-cycle neutrino mass triple
with emitted weighted-cycle absolute splittings recorded in Ref.~\cite{ophparticles}'s exact-output surface. The public Higgs/top pair comes from the source-only split theorem on the declared D10/D11 surface rather than from the compare-only inverse slice, while the repo-wide exact top row is also carried by the selected-class quark theorem.

\paragraph{Extended derivation.}
The structural-to-family route and the full per-sector claim-tier audit are developed in
\emph{Deriving the Particle Zoo from Observer Consistency}~\cite{ophparticles}.

\section{Screen Microphysics, Records, and Observer Continuation}

The screen-microphysics lane is the engineering side of the OPH suite. It asks
whether some microscopic model might exist in principle and gives one explicit regulated
reference architecture: a finite gauge-register or quantum-link style screen model in which local
registers, patches, overlaps, edge observables, records, repair instruments, and observer-facing
interfaces are all made concrete at fixed cutoff.

This lane has five theorem-bearing components. First, the reference architecture itself is
explicit. Second, the regulated patch-net embedding theorem is closed on its fixed-cutoff
object/local-interface surface, and the edge-sector thermal/Casimir branch carries an explicit
fixed-cutoff law with one remaining compact lift above that theorem surface.
Third, the fixed-cutoff measurement/Born-rule package is closed. Fourth, the fixed-cutoff
Bell/CHSH package is closed on the declared two-wing surface. Fifth, the
checkpoint/restoration observer package is closed. The external burdens on this lane are the final
packet-level quotient closure where one wants an autonomous exported dynamics, the compact
heat-kernel lift, global consensus analysis, refinement-stable universality, and the
continuum/gravity lift.

\paragraph{Reference-architecture takeaway.}
The synthesis-level point is that the regulated screen-side architecture supplies a concrete
habitat in which local observables, overlap observables, record registers, and synchronization
maps can all be written without pretending to identify a unique final UV completion.

\paragraph{Imported theorem from Ref.~\cite{ophmicrophysics} (Fixed-cutoff record algebra and Born-L\"uders package).}
For each completed compare/write/verify slice of the regulated microphysics, the declared pointer
and overlap-sector projectors generate a finite commutative central record algebra
\[
\mathcal Z_{\mathrm{rec}}.
\]
Every observer-accessible event \(E\) in that algebra has probability
\[
\mathbb P(E)=\operatorname{Tr}(\rho P_E),
\]
and conditioning on \(E\) gives the operational post-measurement state
\[
\rho\!\mid_E = \frac{P_E \rho P_E}{\operatorname{Tr}(\rho P_E)}.
\]
If a practical readout instead uses projectors \(Q_a\) with commuting central reference
projectors \(\widehat Q_a\) on the same declared slots and
\[
\delta_{\mathrm{rec}}=\max_a \|Q_a-\widehat Q_a\|,
\]
then
\[
\|[Q_a,Q_b]\|\le 4\,\delta_{\mathrm{rec}},
\]
and any accessible-state perturbation \(\|\widetilde\rho-\rho\|_1\le\varepsilon\) changes each
declared elementary record-event probability by at most \(\varepsilon+\delta_{\mathrm{rec}}\).

\paragraph{Imported theorem from Ref.~\cite{ophmicrophysics} (Fixed-cutoff Bell / CHSH package).}
On the declared fixed-cutoff physical observable algebra, fix commuting left/right wing
subalgebras, central binary setting registers, binary projective readouts on each wing, and a
physical source state on the joint wing algebra. Then the compare slice carries the joint law
\[
p(a,b\mid x,y)
=
\operatorname{Tr}\!\bigl(\rho_{LR}\,P_{a|x}^{(L)}P_{b|y}^{(R)}\bigr),
\]
the local marginals are independent of the remote setting, the Bell correlators satisfy
\[
E(x,y)=\operatorname{Tr}\!\bigl(\rho_{LR}\,A_xB_y\bigr),
\]
and the CHSH combination obeys
\[
\bigl|E(0,0)+E(0,1)+E(1,0)-E(1,1)\bigr|
\le
2\sqrt2.
\]
If the source family contains an explicit two-qubit branch with the stated Pauli readouts, the
same fixed-cutoff surface saturates \(2\sqrt2\) exactly on that branch. The source-state premise
is explicit: the theorem derives the Bell law and the Tsirelson bound from the stated
fixed-cutoff operator surface, while Bell-pair preparation and two-qubit factor structure remain
stated branch premises.

\paragraph{Imported theorem from Ref.~\cite{ophmicrophysics} (Checkpoint/restoration and observer backup).}
For an observer patch \(P_O\), let the checkpoint data consist of the observer-facing record
algebra, the accessible local state, the future update schedule, and the externally visible
overlap interface data. Exact restoration reproduces the full future law of observer-accessible
events, while an \(\varepsilon\)-accurate restoration changes that future law by at most
\(\varepsilon\) in total variation.

\paragraph{Observer-facing conclusion.}
The theorem-level content is modest but sharp: OPH supplies a fixed-cutoff measurement interface,
a fixed-cutoff checkpoint/restoration package, and an operational observer-identity criterion on
observer-accessible event algebras. Stronger substrate-selection or strange-loop closure claims
remain outside the recovered theorem package.

\paragraph{Extended derivation.}
The fixed-cutoff edge-law, measurement, Born-rule, Bell/CHSH, and checkpoint/restoration packages are developed in
\emph{Screen Microphysics, Patches, and Observer Synchronization in OPH}~\cite{ophmicrophysics}.

\section{Conditional Worldsheet/String Branch}

The synthesis paper carries the string/worldsheet branch on the same theorem boundary used across
the live OPH papers: a genuine theorem-level bridge from OPH edge sectors to the two-dimensional
Yang-Mills partition function, followed by a conditional large-\(N_{\mathrm{edge}}\) continuation
to a worldsheet reorganization.

\paragraph{Imported theorem (Heat-kernel edge-sector bridge).}
Import the fixed-cutoff same-overlap edge-law package from
\emph{Screen Microphysics, Patches, and Observer Synchronization in OPH}~\cite{ophmicrophysics}.
Under the same overlap-gauge realization and local-Gibbs/MaxEnt edge branch, the edge-sector
weights satisfy
\[
p_R(t)\propto d_R e^{-t C_2(R)}.
\]
Consequently the edge partition function matches the standard two-dimensional Yang-Mills
heat-kernel form.

\paragraph{Imported proof route.}
The microphysics source surface carries the fixed-cutoff thermal/Casimir law on the declared
overlap interface. Peter--Weyl decomposition~\cite{peterWeyl27}
then identifies the resulting sum with the standard heat-kernel expression for
two-dimensional Yang-Mills on the compact-group refinement lift.

\paragraph{Exact bridge identity.}
Writing the closed edge partition function as
\[
Z_{\mathrm{edge}}(t)=\sum_R d_R^2 e^{-tC_2(R)},
\]
Peter--Weyl identifies it with the compact-group heat kernel at the identity,
\[
Z_{\mathrm{edge}}(t)=K_t(1).
\]
The Chapman--Kolmogorov gluing law for \(K_t\) is the precise sense in which collar sewing
matches the two-dimensional Yang--Mills heat-kernel surface before any large-\(N_{\mathrm{edge}}\)
continuation is invoked.

\paragraph{Continuation boundary.}
If a controlled large-\(N_{\mathrm{edge}}\) regime exists, with \(N_{\mathrm{edge}}\) distinct from
the physical color rank \(N_c=3\), then the Gross-Taylor rewriting~\cite{grossTaylor93} gives a genus expansion and a
worldsheet-like reorganization. Critical-superstring claims, worldsheet CFT closure, anomaly
cancellation, and full massless-spectrum matching remain outside the recovered core theorem package.

\paragraph{Higher-gauge continuation slot.}
The genuinely noncentral crossed-module gluing data on cuts provide the natural continuation-level
slot for \(B\)-field / gerbe data in any string-style reorganization of the OPH edge sector. This
is a structural analogy only; it is not yet an open/closed-string boundary formalism or a
critical-string theorem.

\section{Cross-Lane Theorem Boundary and Open Directions}

The state of the OPH suite is:

\begin{enumerate}[leftmargin=2em]
\item The fixed-cutoff collar, higher-gauge, and consensus theorem packages are part of
the closed finite-regulator surface. The genuinely noncentral topological branch is not
fixed-cutoff gap, and the quotient-level repair normal form is explicit on the finite patch-net
surface. The consensus lane is classified there as a finite-state exact theorem package rather
than as a universality claim.
\item The screen-microphysics lane has an explicit regulated reference architecture together
with closed measurement/Born-rule, Bell/CHSH, and checkpoint/restoration packages. Its open fronts
are packet-level quotient closure where a declared observable family is meant to carry an
autonomous exported dynamics, the compact heat-kernel lift, refinement-stable universality,
global consensus closure, and the continuum/gravity lift.
\item Physical UV uniqueness is quotient-level and ancilla-stable: the theorem-grade object is
the family of terminal expectation functionals on the declared physical observable algebras, fixed
modulo implementation hiding and inert ancillary refinement, not a unique microscopic
representative.
\item The Lorentz/null-modular/Einstein chain remains a controlled refinement/scaling-limit
branch. In the canonical premise ledger, the D3 side carries \textbf{T2} together with the
theorem-local realized transported geometric cap-local system whose carried-collar schedule sits
above the transported fixed-local-collar Markov/faithfulness datum, and then ordered cut-pair
rigidity on the extracted prime geometric subnet; on that branch the finite cap regulators are
type-I, but the scaling-limit observer algebra may be non-type-I, so the theorem is
automorphism-level there and \(K_C=2\pi B_C\) is only the special type-I limit form; stronger
BW / canonical-cap phrasing remains theorem-external unless the extraction-and-rigidity package
is supplied. The D4 side still uses theorem-local null-cut
center transfer, the extra inherited left/right strip-split condition needed for the
spatial-collar-type tensor decomposition, the exact-or-controlled Markov hypotheses on one fixed
inherited strip model, and the geometric scaling action on the null half-line blow-up net that
derives the half-sided modular pair, while the same-half-line local modular-Hamiltonian input and
the separate bounded-interval projective branch enter only later; on that D4 surface the
exact-or-controlled strip additivity, the endpoint-Lipschitz renormalized half-line family, the
weak tail generator, the derived half-sided modular inclusion, and the positive null-translation
generator on its Stone domain with the affine half-line modular relation are internal to the
bridge itself; and the D5 side adds fixed-cap stationarity,
the locally Lorentzian \(d=4\) scaling regime, and the tensor-upgrade side conditions.
\item Compact gauge reconstruction and the realized Standard Model quotient remain tied to the
transportability, symmetric-braiding, and fiber-functor premises stated in the canonical
technical-premise list.
\item The particle branch is structurally rich and sector-split: structural carriers and the
realized Standard Model skeleton are fixed, electroweak closure is in hand, the Higgs/top stage
closes on its source-only split theorem surface, the charged-lepton lane carries exact centered
readback plus a closed common-shift no-go, the neutrino lane closes on its weighted-cycle theorem
branch, and the quark and hadron lanes sit on explicit continuation fronts.
\item The string branch is a continuation of the heat-kernel edge-sector theorem, not a promoted
recovered-core result.
\end{enumerate}

\paragraph{Local unification status.}
At the synthesis level, one local unification surface is explicit and one uniform theorem tier for
\(c\), \(G\), \(W\), \(Z\), and \(H\) is absent. The same declared local input \(P\) governs the
electroweak/Higgs trunk and the gravity-side edge-entropy bridge, while the invariant causal speed
\(c\) is structural from the Lorentz branch and gains its SI label only on the local readout
package.

{\centering
\scriptsize
\setlength{\tabcolsep}{3pt}
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.11\textwidth}>{\raggedright\arraybackslash}p{0.25\textwidth}>{\raggedright\arraybackslash}p{0.24\textwidth}>{\raggedright\arraybackslash}p{0.31\textwidth}@{}}
\toprule
Quantity & Best value on the paper surface & Common OPH chain & Caveat \\
\midrule
\(c\) & \(299792458~\mathrm{m/s}\) & structural Lorentz/BW branch \(\rightarrow\) invariant causal speed \(\rightarrow\) local SI readout & structural rather than \(P\)-fitted; the SI presentation sits on the stated BW/Lorentz honesty package \\
\(G\) & \(6.674299995910528\times10^{-11}~\mathrm{m^3\,kg^{-1}\,s^{-2}}\) on the stated local extension surface & \(P \rightarrow \ellbar_{\mathrm{SU(2)}}+\ellbar_{\mathrm{SU(3)}} = \ellbar_{\mathrm{shared}} \rightarrow G_{\mathrm{SI}} = c^3 a_{\mathrm{cell}}/(\hbar P)\) & stated relative to the declared \(a_{\mathrm{cell}}\) datum; on that surface the D10 pixel law fixes \(\ellbar_{\mathrm{shared}}=P/4\), and the strict classical-regime clause remains explicit \\
\(M_W\) & public target-free row \(80.37700001539531~\mathrm{GeV}\); exact sidecar \(80.377~\mathrm{GeV}\) & \(P \rightarrow \alpha_U(P) \rightarrow (t_U(P),t_{\mathrm{tr}}(P)) \rightarrow v(P) \rightarrow\) target-free electroweak repair chart \(\rightarrow M_W\) & exact promotion requires one target-free electroweak chart-identity theorem \\
\(M_Z\) & public target-free row \(91.18797807794321~\mathrm{GeV}\); exact sidecar \(91.18797809193725~\mathrm{GeV}\) & same target-free electroweak trunk & same electroweak chart-identity caveat \\
\(M_H\) & exact D11 split-theorem pair \(M_H=125.1995304097179~\mathrm{GeV}\), \(m_t=172.3523553288312~\mathrm{GeV}\) & same \(P\)-driven electroweak core \(\rightarrow\) D10 repair chart \(\rightarrow\) \(\rho_{HT}\) and source-only split selectors \(\rightarrow\) D11 Jacobian & Higgs row is exact on the declared running, matching, and threshold surface; the inverse sidecar remains compare-only; the bridge to the auxiliary direct-top PDG row is open and is tracked in \href{https://github.com/FloatingPragma/observer-patch-holography/issues/207}{issue \#207} \\
\bottomrule
\end{tabular}
\par}

The exact-release package on that surface is local and finite: the strict classical-regime clause
and the target-free electroweak chart identity for \(W/Z\).
The familiar-unit display split on that same surface is
\[
L_{\mathrm{loc}}=\sqrt{a_{\mathrm{cell}}}\,\widehat L(P),\qquad
t_{\mathrm{loc}}=\frac{\sqrt{a_{\mathrm{cell}}}}{c}\,\widehat T(P),
\]
\[
E_{\mathrm{loc}}=\frac{\hbar c}{\sqrt{a_{\mathrm{cell}}}}\,\widehat E(P),\qquad
\Theta_{\mathrm{loc}}=\frac{\hbar c}{k_B\sqrt{a_{\mathrm{cell}}}}\,\widehat\Theta(P),
\]
with dimensionless \(\widehat L,\widehat T,\widehat E,\widehat\Theta\). The gravity-side
shared-edge identity and the local SI readout are therefore fixed relative to the declared
microscopic datum \(a_{\mathrm{cell}}\), while meters, seconds, GeV, and Kelvin remain downstream
display conventions built from the structural \(c\) row and the familiar constants \(\hbar\),
\(k_B\).

\paragraph{Companion papers.}
Detailed derivations appear in Refs.~\cite{ophcompact,ophconsensus,ophmicrophysics,ophparticles}.

\section{Conclusion}

This paper presents the full framework on one synthesis surface. The five-axiom basis, the
conditional gravity and gauge branches, the consensus formulation, the particle-spectrum branch,
the regulated screen-microphysics lane, the fixed-cutoff measurement and observer package, and the
conditional worldsheet continuation appear on one common synthesis surface.

The suite is uneven but concrete. It has a sharp
fixed-cutoff local picture, a conditional recovered core for relativity and Standard-Model
structure, real particle-side quantitative outputs, and a usable microscopic engineering lane. The
main external burdens are equally explicit: the D3 geometric-cap lift under \textbf{T2}, the D4
null-bridge inputs together with the bounded-interval projective branch, the D5
fixed-cap-stationarity / local-Lorentz tensor-upgrade step, the transportable-sector compact-gauge
lift, the microphysics closure passes, and the matter-family and hadron closure lanes.
Refs.~\cite{ophcompact,ophconsensus,ophmicrophysics,ophparticles} are the depth surfaces for
sector-by-sector proofs, quantitative details, and continuation-level material. The local
cross-lane numerical surface is explicit enough to summarize concisely: one declared input \(P\)
organizes the bosonic mass trunk and the gravity-side shared edge-entropy identity beneath the
emitted local \(G\) row, while the same familiar-unit package reads meters and seconds from the
single ruler \(\sqrt{a_{\mathrm{cell}}}\) together with the structural invariant speed \(c\), and
reads GeV and Kelvin from the inverse local ruler through \(\hbar\) and \(k_B\).
