\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools,bm}
\usepackage{longtable,booktabs,array,multirow}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{framed}
\usepackage{fancyvrb}
\usepackage{ragged2e}
\usepackage{hyperref}
\input{release_info.tex}

% Springer/pdflatex compatibility: provide fallbacks for Unicode math/text glyphs.
\newcounter{none}
\providecommand{\theHnone}{\arabic{none}}
\providecommand{\textsubscript}[1]{$_{\mathrm{#1}}$}
\ifdefined\DeclareUnicodeCharacter
\DeclareUnicodeCharacter{00B1}{\ensuremath{\pm}}
\DeclareUnicodeCharacter{00B2}{\textsuperscript{2}}
\DeclareUnicodeCharacter{00B3}{\textsuperscript{3}}
\DeclareUnicodeCharacter{00B7}{\ensuremath{\cdot}}
\DeclareUnicodeCharacter{00B9}{\textsuperscript{1}}
\DeclareUnicodeCharacter{00D7}{\ensuremath{\times}}
\DeclareUnicodeCharacter{02B8}{\textsuperscript{y}}
\DeclareUnicodeCharacter{0393}{\ensuremath{\Gamma}}
\DeclareUnicodeCharacter{0394}{\ensuremath{\Delta}}
\DeclareUnicodeCharacter{039B}{\ensuremath{\Lambda}}
\DeclareUnicodeCharacter{03A3}{\ensuremath{\Sigma}}
\DeclareUnicodeCharacter{03A6}{\ensuremath{\Phi}}
\DeclareUnicodeCharacter{03A9}{\ensuremath{\Omega}}
\DeclareUnicodeCharacter{03B1}{\ensuremath{\alpha}}
\DeclareUnicodeCharacter{03B2}{\ensuremath{\beta}}
\DeclareUnicodeCharacter{03B3}{\ensuremath{\gamma}}
\DeclareUnicodeCharacter{03B4}{\ensuremath{\delta}}
\DeclareUnicodeCharacter{03B5}{\ensuremath{\varepsilon}}
\DeclareUnicodeCharacter{03B7}{\ensuremath{\eta}}
\DeclareUnicodeCharacter{03B8}{\ensuremath{\theta}}
\DeclareUnicodeCharacter{03BA}{\ensuremath{\kappa}}
\DeclareUnicodeCharacter{03BB}{\ensuremath{\lambda}}
\DeclareUnicodeCharacter{03BC}{\ensuremath{\mu}}
\DeclareUnicodeCharacter{03BD}{\ensuremath{\nu}}
\DeclareUnicodeCharacter{03BE}{\ensuremath{\xi}}
\DeclareUnicodeCharacter{03C0}{\ensuremath{\pi}}
\DeclareUnicodeCharacter{03C1}{\ensuremath{\rho}}
\DeclareUnicodeCharacter{03C3}{\ensuremath{\sigma}}
\DeclareUnicodeCharacter{03C4}{\ensuremath{\tau}}
\DeclareUnicodeCharacter{03C6}{\ensuremath{\phi}}
\DeclareUnicodeCharacter{03C7}{\ensuremath{\chi}}
\DeclareUnicodeCharacter{03C8}{\ensuremath{\psi}}
\DeclareUnicodeCharacter{03C9}{\ensuremath{\omega}}
\DeclareUnicodeCharacter{1D9C}{\textsuperscript{c}}
\DeclareUnicodeCharacter{2020}{\ensuremath{\dagger}}
\DeclareUnicodeCharacter{2070}{\textsuperscript{0}}
\DeclareUnicodeCharacter{2074}{\textsuperscript{4}}
\DeclareUnicodeCharacter{2075}{\textsuperscript{5}}
\DeclareUnicodeCharacter{2076}{\textsuperscript{6}}
\DeclareUnicodeCharacter{2077}{\textsuperscript{7}}
\DeclareUnicodeCharacter{2078}{\textsuperscript{8}}
\DeclareUnicodeCharacter{2079}{\textsuperscript{9}}
\DeclareUnicodeCharacter{207A}{\textsuperscript{+}}
\DeclareUnicodeCharacter{207B}{\textsuperscript{-}}
\DeclareUnicodeCharacter{207D}{\textsuperscript{(}}
\DeclareUnicodeCharacter{207E}{\textsuperscript{)}}
\DeclareUnicodeCharacter{207F}{\textsuperscript{n}}
\DeclareUnicodeCharacter{2080}{\textsubscript{0}}
\DeclareUnicodeCharacter{2081}{\textsubscript{1}}
\DeclareUnicodeCharacter{2082}{\textsubscript{2}}
\DeclareUnicodeCharacter{2083}{\textsubscript{3}}
\DeclareUnicodeCharacter{2085}{\textsubscript{5}}
\DeclareUnicodeCharacter{2086}{\textsubscript{6}}
\DeclareUnicodeCharacter{2087}{\textsubscript{7}}
\DeclareUnicodeCharacter{2088}{\textsubscript{8}}
\DeclareUnicodeCharacter{208B}{\textsubscript{-}}
\DeclareUnicodeCharacter{2102}{\ensuremath{\mathbb{C}}}
\DeclareUnicodeCharacter{210B}{\ensuremath{\mathcal{H}}}
\DeclareUnicodeCharacter{2113}{\ensuremath{\ell}}
\DeclareUnicodeCharacter{2124}{\ensuremath{\mathbb{Z}}}
\DeclareUnicodeCharacter{2192}{\ensuremath{\to}}
\DeclareUnicodeCharacter{2193}{\ensuremath{\downarrow}}
\DeclareUnicodeCharacter{2194}{\ensuremath{\leftrightarrow}}
\DeclareUnicodeCharacter{21D2}{\ensuremath{\Rightarrow}}
\DeclareUnicodeCharacter{2202}{\ensuremath{\partial}}
\DeclareUnicodeCharacter{2208}{\ensuremath{\in}}
\DeclareUnicodeCharacter{220F}{\ensuremath{\prod}}
\DeclareUnicodeCharacter{2212}{\ensuremath{-}}
\DeclareUnicodeCharacter{221A}{\ensuremath{\surd}}
\DeclareUnicodeCharacter{221D}{\ensuremath{\propto}}
\DeclareUnicodeCharacter{221E}{\ensuremath{\infty}}
\DeclareUnicodeCharacter{2229}{\ensuremath{\cap}}
\DeclareUnicodeCharacter{222B}{\ensuremath{\int}}
\DeclareUnicodeCharacter{223C}{\ensuremath{\sim}}
\DeclareUnicodeCharacter{2245}{\ensuremath{\cong}}
\DeclareUnicodeCharacter{2248}{\ensuremath{\approx}}
\DeclareUnicodeCharacter{2261}{\ensuremath{\equiv}}
\DeclareUnicodeCharacter{2264}{\ensuremath{\leq}}
\DeclareUnicodeCharacter{2265}{\ensuremath{\geq}}
\DeclareUnicodeCharacter{226A}{\ensuremath{\ll}}
\DeclareUnicodeCharacter{2272}{\ensuremath{\lesssim}}
\DeclareUnicodeCharacter{2295}{\ensuremath{\oplus}}
\DeclareUnicodeCharacter{2297}{\ensuremath{\otimes}}
\DeclareUnicodeCharacter{2609}{\ensuremath{\odot}}
\DeclareUnicodeCharacter{2713}{\ensuremath{\checkmark}}
\DeclareUnicodeCharacter{27E8}{\ensuremath{\langle}}
\DeclareUnicodeCharacter{27E9}{\ensuremath{\rangle}}
\DeclareUnicodeCharacter{27F9}{\ensuremath{\Longrightarrow}}
\fi

\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}
\setcounter{tocdepth}{3}
\setcounter{secnumdepth}{3}
\setlength{\LTleft}{0pt}
\setlength{\LTright}{0pt}
\setlength{\tabcolsep}{1.2pt}
\setlength{\emergencystretch}{3em}
\renewcommand{\arraystretch}{1.05}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CommentTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\AttributeTok}[1]{#1}
\newcommand{\SU}{\mathrm{SU}}
\newcommand{\U}{\mathrm{U}}

\title{Observers Are All You Need}
\author{B. M\"uller \and Peter Nguyen}
\date{\OPHPaperReleaseDate}

\begin{document}
\maketitle
\OPHPaperReleaseBanner

\begin{abstract}
Observer-Patch Holography (OPH) is a mathematical reconstruction program that starts from a simple requirement: overlapping local observer descriptions on a holographic screen must agree where they overlap. From that starting point, we develop conditional routes toward general relativity, toward reconstruction of the Standard Model gauge structure, toward a first-principles particle-mass program, and toward string/worldsheet descriptions emerging from the same underlying framework. We also report early IBM Quantum Cloud benchmarks of OPH-motivated reduced sectors that match the predicted recoverability ordering and exact-ratio patterns on real hardware, providing preliminary experimental support for the local OPH picture. Claim-tier authority remains with the compact submission paper; this wrapper broadens the exposition without upgrading those tiers. In the interpretive epilogue, we examine the strange-loop hypothesis that, under OPH, the universe can exist as a self-referential timeless causal structure in which observer reconstruction and information constraints close into a single consistency loop. Throughout, theorem-level results, conditional branches, quantitative continuations, experimental benchmarks, and interpretive material are kept explicitly distinct.
\end{abstract}

\tableofcontents
\newpage

\part{Core Framework and Axioms}
\input{tex_fragments/PAPER.tex}

\clearpage
\part{Gauge Group Derivation}
\input{tex_fragments/GAUGE_GROUP_DERIVATION.tex}

\clearpage
\part{Spectrum Derivation}
\input{tex_fragments/SPECTRUM_DERIVATION.tex}

\clearpage
\part{String-Theory Derivation}
\input{tex_fragments/STRING_THEORY.tex}

\clearpage
\part{Technical Supplement}
\input{tex_fragments/TECHNICAL_SUPPLEMENT.tex}

\clearpage
% Parts I-V carry synchronized derivation and supplement material; later parts are interpretive or speculative appendices and do not alter the compact paper's claim tiers.
\part{Interpretive Appendix: Strange-Loop Proposal}

\section{Interpretive Status, the Habitat Theorem, and the Remaining Strange-Loop Gap}
This part is an interpretive epilogue, outside the Phase-I recovered core and the D10--D11 supplement-backed implementation. OPH supplies the ambient state-and-law habitat needed for a fixed-point wrapper. This section leaves the actual closure map on the stronger observer-supporting sector open.

The OPH inputs used here are all internal to the synchronized paper set:
\begin{enumerate}
\item the patch net \(P\mapsto A(P)\) of von Neumann algebras together with isotony and overlap restriction maps;
\item the global state on the inductive-limit algebra, whose restrictions witness a nonempty overlap-consistent local sector;
\item the finite Axiom-3 MaxEnt/refinement branch, which supplies a common finite family of gauge-invariant local constraint observables across cutoffs;
\item on the fixed-cutoff branch, the derived finite type-I presentations and compact boundary gluing groups already used elsewhere in the OPH package.
\end{enumerate}

The law slot is encoded by the finite expectation-value coordinates of the retained Axiom-3 constraint family. That choice furnishes a compact convex state-and-law habitat within OPH.

\paragraph{Theorem (OPH internal state-and-law habitat theorem).}
Fix finitely many screen patches \(P_1,\dots,P_N\) in the standard OPH setup. For each \(i\), let
\[
M_i:=A(P_i),
\qquad
M_{ij}:=A(P_i\cap P_j),
\]
where \(M_i\) is the patch von Neumann algebra and \(M_{ij}\subset M_i,M_j\) is the overlap algebra. Let
\[
S_i:=S(M_i)\subset M_i^*
\]
be the full state space of \(M_i\), endowed with the weak* topology \(\sigma(M_i^*,M_i)\).

Choose a finite family of self-adjoint gauge-invariant local constraint observables
\[
\mathcal O=\{O_1,\dots,O_m\}
\]
from the Axiom-3 MaxEnt branch, with each \(O_a\) supported in one of the chosen patches; write \(i(a)\) for an index such that \(O_a\in M_{i(a)}\).

Define the overlap-consistent state sector
\[
X_{\mathrm{ov}}
:=
\left\{
(\omega_1,\dots,\omega_N)\in \prod_{i=1}^N S_i:
\omega_i|_{M_{ij}}=\omega_j|_{M_{ij}}\ \text{for all }i,j
\right\}.
\]
Define the OPH law-coordinate map
\[
c:X_{\mathrm{ov}}\to \mathbb R^m,
\qquad
c(\omega_1,\dots,\omega_N)
:=
\bigl(\omega_{i(1)}(O_1),\dots,\omega_{i(m)}(O_m)\bigr).
\]
Let
\[
X_{\mathcal O}
:=
\left\{
(\omega_1,\dots,\omega_N,\ell)\in
\left(\prod_{i=1}^N S_i\right)\times \mathbb R^m:
(\omega_1,\dots,\omega_N)\in X_{\mathrm{ov}},
\ \ell=c(\omega_1,\dots,\omega_N)
\right\}.
\]
Then:
\begin{enumerate}
\item the ambient product
\[
E:=
\left(\prod_{i=1}^N M_i^*\right)\times \mathbb R^m
\]
is a Banach space for any product norm;
\item \(X_{\mathcal O}\) is nonempty and convex;
\item \(X_{\mathcal O}\) is norm-closed in \(E\);
\item \(X_{\mathcal O}\) is compact in the product topology
\[
\tau
:=
\left(\prod_{i=1}^N \sigma(M_i^*,M_i)\right)\times
\text{Euclidean topology on }\mathbb R^m;
\]
\item therefore every \(\tau\)-continuous self-map
\[
\Phi:X_{\mathcal O}\to X_{\mathcal O}
\]
has a fixed point.
\end{enumerate}

\begin{proof}
Each \(M_i\) is a von Neumann algebra in the OPH patch net, hence a Banach space, so each dual \(M_i^*\) is Banach. A finite product of Banach spaces is Banach, hence so is \(E\).

For each \(i\), the state space
\[
S_i=\{\omega\in M_i^*:\omega\ge 0,\ \omega(1)=1\}
\]
is convex and weak* compact by Banach--Alaoglu, because it is a weak* closed subset of the dual unit ball. For every pair \((i,j)\), restriction along \(M_{ij}\subset M_i\) and \(M_{ij}\subset M_j\) defines affine weak* continuous maps
\[
r_{ij}:S_i\to S(M_{ij}),
\qquad
r_{ji}:S_j\to S(M_{ij}).
\]
Hence \(X_{\mathrm{ov}}\) is an intersection of affine equalizer sets, so it is convex and \(\tau\)-closed inside \(\prod_i S_i\). Since \(\prod_i S_i\) is compact and convex in the product weak* topology, \(X_{\mathrm{ov}}\) is compact and convex as well.

Nonemptiness comes from the OPH global state on the inductive-limit algebra: its restrictions
\[
\bigl(\omega|_{M_1},\dots,\omega|_{M_N}\bigr)
\]
belong to \(X_{\mathrm{ov}}\) because the restrictions agree on every overlap by construction.

Each coordinate \(\omega_{i(a)}\mapsto \omega_{i(a)}(O_a)\) is affine and weak* continuous, since evaluation at a fixed algebra element is weak* continuous. Thus \(c\) is affine and \(\tau\)-continuous. The graph map
\[
G:X_{\mathrm{ov}}\to E,
\qquad
G(x):=(x,c(x)),
\]
is affine and continuous, so its image \(X_{\mathcal O}=G(X_{\mathrm{ov}})\) is convex and \(\tau\)-compact.

To see norm-closedness in \(E\), let \((x_n,c(x_n))\to (x,\ell)\) in norm. Norm convergence implies weak* convergence on each coordinate, so \(x\in X_{\mathrm{ov}}\) because \(X_{\mathrm{ov}}\) is weak* closed. Since \(c\) is weak* continuous, \(c(x_n)\to c(x)\), while norm convergence in \(\mathbb R^m\) also gives \(c(x_n)\to \ell\). Hence \(\ell=c(x)\), so \((x,\ell)\in X_{\mathcal O}\).

Finally, \(X_{\mathcal O}\) is a compact convex subset of the locally convex topological vector space \(E\) equipped with \(\tau\). Therefore every \(\tau\)-continuous self-map \(\Phi:X_{\mathcal O}\to X_{\mathcal O}\) has a fixed point by the Schauder--Tychonoff fixed-point theorem.
\end{proof}

\paragraph{Corollary (Fixed-cutoff OPH Brouwer corollary).}
Assume the fixed-cutoff regulator realization \(R0/R1\): each chosen patch algebra \(M_i=A(P_i)\) is finite-dimensional. Then \(E\) is finite-dimensional, the weak* and norm topologies coincide on \(E\), and \(X_{\mathcal O}\) is a nonempty compact convex subset of a finite-dimensional real vector space. Hence every continuous self-map
\[
\Phi:X_{\mathcal O}\to X_{\mathcal O}
\]
has a fixed point by Brouwer. If, moreover, \(\Phi\) is a contraction for some metric on \(X_{\mathcal O}\), then the fixed point is unique and the iterates converge to it from every starting point by Banach's contraction theorem.

\begin{proof}
Under \(R0/R1\), the OPH fixed-cutoff branch identifies each chosen patch algebra with a finite-dimensional type-I presentation modulo compact boundary redundancy, so each \(M_i\) and \(M_i^*\) is finite-dimensional. Hence \(E\) is finite-dimensional and all relevant locally convex topologies coincide. The habitat theorem above shows that \(X_{\mathcal O}\) is nonempty, compact, and convex, so Brouwer gives a fixed point for every continuous self-map. The contraction statement is the usual Banach fixed-point theorem.
\end{proof}

What still remains outside the scientific core is:
\begin{enumerate}
\item an actual OPH closure map \(\Phi\) built from already-internal operations such as overlap repair, Axiom-3 MaxEnt reprojection, collar recoverability, and record-sector coarse-graining;
\item a proof that the stronger ``observer-supporting'' or ``selected-world'' criteria carve out a nonempty compact convex \(\Phi\)-invariant subset of \(X_{\mathcal O}\);
\item any uniqueness, contraction, or Lyapunov-type stability estimate for that closure map.
\end{enumerate}

The habitat theorem above supplies the ambient Banach/compact-convex setting. The strange-loop continuation still requires the theorem-level closure map and the stronger invariant-sector and stability inputs.

\section{Timeless Causal Chain}
The hypothesis is represented by the chain
\[
\begin{aligned}
\text{information constraints}
&\to \text{effective physics}
\to \text{complex chemistry and biology}\\
&\to \text{observers with records}
\to \text{formal OPH reconstruction}\\
&\to \text{OPH-compatible simulation substrate}
\to \text{information constraints}.
\end{aligned}
\]
In this paper the chain is interpreted as a consistency loop, not as a linear first-cause narrative. The Escher drawing-hands analogy is a geometrical metaphor for this closure structure.

\section{Why Reality Exists and Why It Has This Form}
Under this hypothesis, existence is identified with nontrivial fixed points of the OPH consistency map. The observed form of reality is selected by stability requirements:
\begin{enumerate}
\item overlap-consistent sharable records,
\item recoverability under local information loss,
\item long-lived structured sectors that support observer formation,
\item internal reconstructibility of the governing rule set.
\end{enumerate}
The appearance of intelligent observers is therefore not an external add-on. It is part of the closure mechanism itself. Observer-capable worlds are the sectors that complete the loop.

\section{Additional Problem Closures}
This wrapper is a synchronized surface, not a separate claim escalator. The authoritative claim-tier boundary remains the compact note's ledger and Part~I Section~8. In particular, the recovered core is D1--D5 together with D7--D9; D6 is a separate input-dependent corollary; D10--D11 are the current supplement-backed numerical implementation; and D12 collects deferred continuations. Table~\ref{tab:additional-closures} records the status of the broader ``problem closure'' claims that appear in the synthesis essays.

\begin{longtable}{p{0.24\textwidth} p{0.19\textwidth} p{0.50\textwidth}}
\caption{Problem-closure statements sorted by current claim tier.}\label{tab:additional-closures}\\
\toprule
Problem domain & Current status & OPH mechanism / scope note \\
\midrule
\endfirsthead
\toprule
Problem domain & Current status & OPH mechanism / scope note \\
\midrule
\endhead
\bottomrule
\endfoot
Quantum gravity consistency & Phase I recovered core (conditional scaling-limit) & Conditional Lorentz and Jacobson-type Einstein branches from modular geometry, the null bridge, and fixed-cap stationarity. \\
Measurement problem & Interpretive or organizational synthesis & Record algebras and edge-center sectorization motivate these closures, but this wrapper does not upgrade them to the recovered-core tier of the compact note. \\
Cosmological principle and horizon homogeneity & Interpretive or organizational synthesis & MaxEnt state selection under symmetric constraints motivates isotropy and homogeneity stories, but those are not independent Phase-I theorems. \\
Problem of time & Interpretive or organizational synthesis & Modular flow from the BW$_{S^2}$ geometric branch (Theorem~4.2 in the compact note) provides a physical time parameter for each observer patch; this remains a useful organizational principle, not a separate recovered-core theorem in this wrapper. \\
Supersymmetry non-observation vs.\ unification & Phase II current implementation & MSSM-like \(\beta\)-shift comparisons from edge-sector weighting belong to the D10 calibration layer, not to the recovered-core theorem package. \\
Black-hole information paradox & Program-level structural continuation & Edge-center sectorization and recoverability suggest an internal resolution, but the full black-hole-information branch is not part of Phase I. \\
Cosmological constant problem & Phase II input-dependent corollary & \(\Lambda\) is tied to global screen capacity once the screen-capacity identification is adopted; this is not a local recovered-core output. \\
Magnetic monopole expectation from simple GUT groups & Phase I recovered core & The realized product-group branch \(\SU(3)\times\SU(2)\times\U(1)/\mathbb Z_6\) removes the standard simple-GUT symmetry-breaking monopole channel. \\
Proton stability and proton spin fraction & Mixed: Phase I / Phase III & No gauge-mediated proton decay follows from the realized product-group branch (the product-group corollary from the compact paper removes the standard simple-GUT proton-decay channel); proton spin requires nonperturbative QCD completion and is not part of Phase I. \\
Dark matter phenomenology & Phase III deferred continuation & Modular-anomaly response laws remain conjectural beyond the recovered gravity chain. \\
Baryon asymmetry scale & Phase III deferred continuation & Suppression-counting estimates are not a substitute for a derived out-of-equilibrium mechanism. \\
Three generations and Koide structure & Mixed: Phase I / Phase III & \(N_g=3\) is recovered on the realized MAR-admissible branch; Koide and charged-lepton fits require extra flavor ans\"atze. \\
String/worldsheet reorganization & Phase III deferred continuation & Requires a controlled large-\(N_{\mathrm{edge}}\) regime distinct from the physical color rank \(N_c=3\). \\
Why anything exists / strange-loop closure & Interpretive epilogue only & Part~VI gives an OPH-internal state-and-law habitat theorem: overlap-consistent patch states together with finite Axiom-3 law coordinates form a theorem-usable nonempty compact convex sector, and fixed-cutoff branches admit a Brouwer version. The further inputs are the actual OPH closure map on an invariant observer-supporting sector, together with uniqueness and stability. \\
\end{longtable}

\section{Standalone Status}
This wrapper is standalone only in the documentary sense: every derivation cited here appears somewhere in the manuscript, so no external derivation document is required to follow the chain of references. It is \emph{not} a separate authority for claim tier.

For claim-tier purposes, the authoritative ledger is the compact note's ``Results at a Glance'' / ``Predictive Status and Falsifiability'' pair together with Part~I Section~8. In that three-phase program, the recovered core is D1--D5 together with D7--D9; D6 is a separate input-dependent corollary; D10--D11 are the current supplement-backed numerical implementation; and D12 collects deferred continuations. This wrapper should be read as a synchronized compilation surface that inherits those statuses rather than upgrading them.

\clearpage
\part{Speculative Appendix: Observer Continuation and Backup}

This part is a program-level continuation note. It is not part of the Phase-I recovered core, not part of the D10--D11 supplement-backed implementation, and not a theorem-level output of the compact-note authority. The formulas below record one possible OPH-motivated continuation mechanism and its algebraic prerequisites; they do not by themselves establish a recovered observer-continuation theorem.

\section{Observer as Algebraic Pattern}
In OPH, an observer is represented by
\[
O=(P,\mathcal{A}(P),\rho,R),
\]
where $P$ is a screen patch, $\mathcal{A}(P)$ is its local algebra, $\rho$ is the local state, and $R$ is the record algebra. Records are implemented by approximately commuting projectors in overlap centers, so they are shareable without violating no-cloning constraints for generic quantum states.

\section{Markov Collar Factorization}
For a collar tripartition $A$-$B$-$D$ with conditional mutual information $I(A:D|B)\le\varepsilon$, the exact Markov limit gives
\[
\rho_{ABD}
=\bigoplus_{\alpha} p_{\alpha}\,
\rho^{(\alpha)}_{A b_L^{\alpha}}
\otimes
\rho^{(\alpha)}_{b_R^{\alpha} D}.
\]
The sector label $\alpha$ is classical center data. This decomposition is the mathematical basis for extracting an interior observer state with a controlled boundary interface.

\section{Checkpoint and Restoration Map}
A checkpoint is the tuple
\[
\mathcal{C}=\bigl(R,\alpha,\rho_{\mathrm{int}}^{(\alpha)}\bigr),
\]
with $\rho_{\mathrm{int}}^{(\alpha)}$ the interior conditional state. Given a compatible target environment state $\sigma_{\mathrm{env}}^{(\alpha)}$, a restored state is
\[
\rho_{\mathrm{new}}^{(\alpha)}
=
\rho_{\mathrm{int}}^{(\alpha)}
\otimes
\sigma_{\mathrm{env}}^{(\alpha)}.
\]
For approximate Markov collars, recovery is controlled by the standard bound
\[
\left\|
\rho_{ABD}
-
(\mathrm{id}_A\otimes\mathcal{R}_{B\to BD})(\rho_{AB})
\right\|_1
\le
2\sqrt{\ln 2\,\varepsilon}.
\]
This gives quantitative trace-distance control on the recovered state under finite conditional mutual information (finite collar error). Interpreting that control as observer continuation requires additional modeling assumptions beyond the bound itself.

\section{Physical Meaning}
The continuation mechanism is a program-level construction motivated by the OPH algebraic structure. If an engineered OPH-compatible substrate exists, observer-state backup and restoration can be formulated in a principled way from sectorized gluing, central records, and recoverability, but the present wrapper does not yet prove a standalone observer-continuation theorem.

\end{document}
